---
title: "ReCalibration 2_10"
output: html_document
---

```{r global_options, include=FALSE}
#global settings
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

```{r, include = FALSE}
#Packages
library(tidyverse)
library(lubridate)
library(SAVER)
```

2/11
Performed more robust calibration method, now need to produce calibration curves and apply to the correct sensors

workflow:
-download and read in data using old code
-devise a way to incorporate actual temps into df
-use obs vs act for each sensor to run a linear regression
-save linear regression for each sensor
-apply linear regressions to the corresponding sensor data from summer deployment

```{r}
#read in data
#removed 15- ULB4HB- super messed up, sensor was broken
files <- list.files(path = "Calibration data 2_6_20/")
sites <- read.csv("site_temps_7_11.csv", header = T, sep = ",")
    sites$f.col.time <- mdy_hm(sites$collection.time)
    sites$f.dep.time <- mdy_hm(sites$deploy.time)
#read in all temps into one dataframe
for (i in 1:length(files)) {
    data <- read.csv(paste0("Calibration data 2_6_20/",
                            files[i]), 
                     skip = 19, 
                     header = T, sep = ",")
    #formatting time
    data$fdates <- mdy_hms(data$Date.Time)
    #making a column with sensor number
    data$sensor <- files[i]
    data$sensor <- gsub("data","\\1", data$sensor)
    data$sensor <- gsub(".csv","\\1", data$sensor)
    #making column with site loc
    #round temperatures to nearest tenth
    data$rnd.dates <- round_date(data$fdates, "5 minutes")
  
  if(i == 1)alldat <- data                 
  if(i > 1)alldat <- rbind(alldat, data)
}
#remove all temps that are not from 2-6-20
    #make column with day component
alldat$day <- day(alldat$rnd.dates)
#remove everything that wasn't on the 6th
obs <- filter(alldat, day == c("6"))
#remove values that aren't at the same time as actual measurements
act <- read.csv("measured temps 2_6.csv")
    #round times to the nearest 5 mins
act$time <- mdy_hm(act$time)
act$r.time <- round_date(act$time, unit = "5 minutes")
    #filter out values that are not within the calibration period
obs <- filter(obs, rnd.dates %in% act$r.time)
#add act measurements to obs
act1 <- select(act, digital, analog, r.time)
obs1 <- select(obs, Value, sensor, rnd.dates)%>%
  rename(r.time = rnd.dates)

comb <- left_join(obs1, act1, by = "r.time")

#run linear regressions
  #make for loop that runs linear regs for each sensor and produces a data frame with coefficients
#list of sensors
sensors <- unique(comb$sensor)
for(k in 1:length(sensors)){
  sensor <- sensors[k]
  df <- filter(comb, sensor == sensors[k])
  reg <- lm(Value ~ digital,
            data = df)
  r2 <- summary(reg)$r.squared
  co <- coefficients(reg)
  #output
  
  temp <- data.frame(sensor = sensor, r2 = r2, intercept = co[1], slope = co[2])
  if(k == 1) all <- temp
  if(k > 1) all <- rbind(all, temp)
}
row.names(all) <- 1:nrow(all)
calibrations <- all

#write.csv(calibrations, file = "calibrations.2_12_20.csv")
```

Successfully calculated curves to correct data, now need to apply corrections
```{r}
#read in og data
cali <- read.csv("calibrations.2_12_20.csv")
fog <- read.csv("Formatted.temps.tall_7_17.csv")

#remove sensor 38
#cali <- filter(cali, sensor != "138")
#seeing which sensors I am missing
deployed <- unique(fog$sensor)
calibrated <- unique(cali$sensor)
diff <- setdiff(deployed, calibrated)

deployed <- as.integer(unique(fog$sensor))
calibrated <- as.integer(unique(cali$sensor))
diff <- setdiff(deployed, calibrated)
#remove sensors I wasn't able to calibrate
fog1 <- filter(fog, sensor %in% calibrated)
#add coeffs to data
cali.fog <- inner_join(fog, cali, by = "sensor")
#create column of corrected values
cali.fog$temp.cor <- ((cali.fog$Value * cali.fog$slope) + cali.fog$intercept)

cali.fog.dayz <- select(cali.fog, temp.cor, rnd.dates, site, type, shed)
cali.fog.dayz$rnd.dates <- ymd_hms(cali.fog.dayz$rnd.dates)
```

Basic time series
```{r}
#formatting time to beginning and end of deployment period
#start <- mdy_hm("6-25-19 12:10")
#end <- mdy_hm("7-5-19 12:10")
#timeseries <- filter(cali.fog.dayz, rnd.dates >= start)
#timeseries <- filter(cali.fog.dayz, rnd.dates <=

ULB <- filter(cali.fog.dayz, shed == "ULB")
ulb.sites <- unique(ULB$site)
GG <- filter(cali.fog.dayz, shed == "GG")
gg.sites <- unique(GG$site)
RMO <- filter(cali.fog.dayz, shed == "RMO")
rmo.sites <- unique(RMO$site)
MUL <- filter(cali.fog.dayz, shed == "MUL")
mul.sites <- unique(MUL$site)


gg.char <- as.character(gg.sites)
ulb.char <- as.character(ulb.sites)
rmo.char <- as.character(rmo.sites)
mul.char <- as.character(mul.sites)
all.ts <- c(gg.char, ulb.char, rmo.char, mul.char)
double <- c("W600B", "LS180B", "W400B", "GC100B", "LS0B", "MUL2HB", "RMO1HB", "RMO2CA", "RMO2HB", "ULB3CB" )

one.each <- setdiff(all.ts, double)
#for initial assessment  

timeseries <- cali.fog.dayz %>% filter(site %in% one.each)
timeseries$site <- gsub('.{1}$', '', timeseries$site)
timeseries$site <- gsub('.{1}$', '', timeseries$site)

feed <- timeseries %>% mutate_each(list(as.character), site, type, shed)
feedy <- feed %>%
  mutate(type = replace(type, type == "channel", "Downstream"),
         type = replace(type, type == "head", "Head"),
         site = replace(site, site == "W60", "Wind"),
         site = replace(site, site == "W40", "Wind"),
         site = replace(site, site == "GC10", "Glac"),
         site = replace(site, site == "GC30", "Glac"),
         site = replace(site, site == "LS", "Land"),
         site = replace(site, site == "LS18", "Land"))

#Before I can plot airT stuff I need to get some kind of AirT data into my df
#comine datasets by time and shed
temps.air <- filter(feedy, type == "air") %>% 
  select(shed, temp.cor, rnd.dates) %>% 
  rename(airT = temp.cor)

doob <- filter(feedy, type != "air")

#brush is the new master datasheet
brush <- left_join(doob, temps.air, by = c("shed", "rnd.dates"))
#read in topo metrics attached to old data
dogg <- read.csv("Tempsanddata_11_8.csv")
dg <- select(dogg, Site, type, UAA..ft2., slope.mean, elev.mean)%>%
  rename(site = Site)
yg <- unique(dg)
row.names(yg) <- 1:nrow(yg)
#removing the duplicate mul2
ug <- slice(yg, -7)%>%
  select(-type)%>%
  mutate_each(list(as.character), site)

#brush includes downstream temps
rug <- filter(brush, type == "Downstream")%>%
  select(temp.cor, rnd.dates, site)%>%
  rename(downT = temp.cor)
hug <- filter(brush, type == "Head")

#testing trying to figure out what is happening
test <- filter(rug, rnd.dates == "2019-06-15 10:10:00")
#need to join topo from ug, downstream temps from rug, everything from hug
hugrug <- left_join(hug, rug, by = c("site", "rnd.dates"))
hugrugug <- left_join(hugrug, ug, by = c("site"))

#write.csv(hugrugug, file = "cor_data_and_topo_2_19.csv")

ulb.ts <- brush %>% filter(shed == "ULB")
mul.ts <- brush %>% filter(shed == "MUL")
rmo.ts <- brush %>% filter(shed == "RMO")
gg.ts <- brush %>% filter(shed == "GG")
#ulb
rmo.ts.plot <- ggplot(data = rmo.ts)+
  geom_line(aes(x = rnd.dates,
                y = temp.cor,
                
                color = site,
                linetype = type), 
            size = 1)+
  scale_linetype_manual(labels = c( "Downstream","Head"),
                        values=c("solid", "dotted"),
                        name = "Location")+
   scale_color_brewer(palette = "Dark2",
                     name = "Stream")+
  xlab(" ")+
  ylab("Temperature (C)")+
  ylim(9, 19)+
  theme_classic()+
  theme(text= element_text(size=17),
        axis.text.x = element_text(size = 17),
        axis.text.y = element_text(size = 17))
rmo.ts.plot
#rmo
ulb.ts.plot <- ggplot(data = ulb.ts)+
  geom_line(aes(x = rnd.dates,
                y = temp.cor,
                color = site,
                linetype = type), 
            size = 1.5)+
  scale_color_brewer(palette = "Dark2",
                     name = "Stream")+
  scale_linetype_manual(values=c("solid", "dotted"),
                        name = "Location",
                        labels = c("Downstream", "Head"))+
  xlab( " ")+
  ylab("Temperature (C)")+
  ylim(9, 19)+
  theme_classic()+
  theme(text= element_text(size=17),
        axis.text.x = element_text(size = 17),
        axis.text.y = element_text(size = 17))+
  guides(color = guide_legend(order = 1), 
              linetype = guide_legend(order = 2))
ulb.ts.plot 
#mul
mul.ts.plot <- ggplot(data = mul.ts)+
  geom_line(aes(x = rnd.dates,
                y = temp.cor,
                color = site,
                linetype = type), 
            size = 1.5)+
  scale_color_brewer(palette = "Dark2",
                     name = "Stream")+
  scale_linetype_manual(values=c( "dotted","solid"),
                        name = "Location",
                        labels = c("Head", "Downstream"))+
  xlab( " ")+
  ylab("Temperature (C)")+
  ylim(9, 19)+
  theme_classic()+
  theme(text= element_text(size=17),
        axis.text.x = element_text(size = 17),
        axis.text.y = element_text(size = 17))
mul.ts.plot
#gg
gg.names <- data.frame("names" =c("Wind","Glacier", "Glacier","Landslide","Wind","Landslide"), 
                       "site" = c("W40","GC10","GC30","LS18","W60","LS"))
gg.ts <- gg.ts %>% inner_join(gg.names, brush, by = "site")

gg.ts.plot <- ggplot(data = gg.ts, aes(x = rnd.dates,
                y = temp.cor,
                color = site))+
  geom_line(aes(linetype = type), size = 1.5)+
  scale_color_brewer(palette = "Dark2",
                     name = "Stream")+
  scale_linetype_manual(values=c("solid", "dotted"),
                        name = "Location",
                        labels = c("Downstream", "Head"))+
  xlab( " ")+
  ylab("Temperature (C)")+
  ylim(9, 19)+
  theme_classic()+
  theme(text= element_text(size=17),
        axis.text.x = element_text(size = 17),
        axis.text.y = element_text(size = 17))
gg.ts.plot




#ggsave("ulb.ts.png", plot = ulb.ts.plot, width = 8, height = 5, units = c("in"))
#ggsave("mul.ts.png", plot = mul.ts.plot, width = 8, height = 5, units = c("in"))
#ggsave("rmo.ts.png", plot = rmo.ts.plot, width = 8, height = 5, units = c("in"))
#ggsave("gg.ts.png", plot = gg.ts.plot, width = 8, height = 5, units = c("in"))

```

```{r}
#making plots for story board
#use "cor_data_and_topo_2_19.csv"
pot <- read.csv("cor_data_and_topo_2_19.csv")
pot$rnd.dates <- ymd_hms(pot$rnd.dates)

#adding averages
pote <- pot%>%
  group_by(site)%>%
  summarise(avg.headtemp = mean(temp.cor, na.rm = TRUE), 
            avg.airtemp = mean(airT),
            med.headtemp = median(temp.cor, na.rm = TRUE),
            med.airtemp = median(airT))

potet <- inner_join(pot, unique(pote), by = c("site"))%>%
  distinct()

#converting topo metrics to metrics
potet <- mutate(potet, elev.mean.meters = elev.mean * 0.3048,
               uaa.m2 = UAA..ft2. * 0.3048 * 0.3048)

format.potet <- select(potet, temp.cor, rnd.dates, site, type, shed, airT, downT, slope.mean, elev.mean.meters, uaa.m2, avg.headtemp, avg.airtemp, med.headtemp, med.airtemp)

#write.csv(format.potet, file = "data.for.analysis_3_4.csv")
#plot drainage area vs all temps
#outlier is probably ls- from spikes in temps that correspond with precip- remove them?
gronk1 <- ggplot(potet, aes(y = med.headtemp,
                             x = uaa.m2,
                             color = shed))+
  geom_point(aes(),
                 size = 4)+
  theme_classic()+
  scale_color_brewer(palette = "Dark2")+

  xlab("drainage area (m2)")
gronk1

gronk1a <- ggplot(potet, aes(y = med.airtemp,
                             x = uaa.m2,
                             color = shed))+
  geom_point(aes(),
                 size = 4)+
  theme_classic()+
  scale_color_brewer(palette = "Dark2")+

  xlab("drainage area (m2)")
gronk1a


#plot mean slope vs temps
gronk2 <- ggplot(potet, aes(y = med.headtemp,
                             x = slope.mean,
                             color = shed))+
  geom_point(aes(),
                 size = 4)+
  theme_classic()+
  scale_color_brewer(palette = "Dark2")+

  xlab("slope (deg)")
gronk2

#plot mean elev vs temps
gronk3 <- ggplot(potet, aes(y = med.headtemp,
                             x = elev.mean.meters,
                             color = shed))+
  geom_point(aes(),
                 size = 4)+
  theme_classic()+
  scale_color_brewer(palette = "Dark2")+

  xlab("mean elev (m)")
gronk3

#how different are the median values from the mean values?
ggplot(potet, aes(x = avg.headtemp,
                  y = med.headtemp))+
  geom_point(aes(color = site), size = 2)+
  geom_abline(slope = 1, intercept = 0, color = "black")+
  theme_classic()
```

```{r}
theme_invis <- function (){
        theme(text= element_text(size=17),
        panel.background  = element_blank(),
        plot.background = element_rect(fill="transparent", colour=NA),
        legend.background = element_rect(fill="transparent", colour=NA),
        legend.key = element_rect(fill="transparent", colour=NA),
        panel.border = element_blank(), panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(), axis.line = element_line(colour = "black", 
                size = rel(1)))
}

shed.breaks <- c("GG","ULB","RMO","MUL")
shed.colors <- c("firebrick4","slateblue4","sienna2","seagreen1")

#plotting slope vs avg water T
elev <- ggplot(potet, aes(x = elev.mean.meters,
                          y = med.headtemp,
                          color = shed))+
  geom_point(size = 4)+
  #geom_smooth(method = 'lm', se = FALSE)+
  theme_classic()+
  theme_invis()+
  labs(x = "Mean Elevation (m)",
       y = "Median WaterT (C)")+
  scale_color_manual(breaks = shed.breaks,
                    values = shed.colors)
elev
#slope
slope <- ggplot(potet, aes(x = slope.mean,
                          y = med.headtemp,
                          color = shed))+
  geom_point(size = 4)+
  #geom_smooth(method = 'lm', se = FALSE)+
  theme_classic()+
  theme_invis()+
  labs(x = "Mean Slope (%)",
       y = "Median WaterT (C)")+
  scale_color_manual(breaks = shed.breaks,
                    values = shed.colors)
slope
#drainage area
drain <- ggplot(potet, aes(x = uaa.m2,
                          y = med.headtemp,
                          color = shed))+
  geom_point(size = 4)+
  #geom_smooth(method = 'lm', se = FALSE)+
  theme_classic()+
  theme_invis()+
  labs(x = "Drainage Area (m2)",
       y = "Median WaterT (C)")+
  scale_color_manual(breaks = shed.breaks,
                    values = shed.colors)
drain

ggsave(drain, filename = "Ctopoplot1.png", bg = "transparent"
       ,width = 5, height = 4, units = c("in"))
ggsave(slope, filename = "Ctopoplot2.png", bg = "transparent"
       ,width = 5, height = 4, units = c("in"))
ggsave(elev, filename = "Ctopoplot3.png", bg = "transparent"
       ,width = 5, height = 4, units = c("in"))
```

```{r}
#make table of regression results for storyboard
all <- lm(avg.headtemp ~ uaa.m2 + elev.mean.meters + slope.mean, data = potet)
summary(all)

t <- lm(avg.headtemp ~ slope.mean, data = potet)
summary(t)

```
```{r}
#rate plots for storyboard
warm <- read.csv("straightlinerates11_8.csv")

rat <- select(warm, Site, straight.line.Dist.to.head.m)%>%
  rename(site = Site)%>%
  mutate_each(list(as.character), site)


rate <- left_join(potet, rat, by = "site")

ratet <- 
```

3/4/20
Figure out if the temperatures at Glacier are real
Compare to old data
```{r}
#use "data.for.analysis_3_4.csv"
potet <- read.csv("data.for.analysis_3_4.csv")

#read in old data
fall <- read.csv("GG Temperature Data Sheets/Falltempfinal.csv")
spring <- read.csv("GG Temperature Data Sheets/Springtempfinal.csv")

means <- c(mean(fall$GC0AF), mean(fall$GC0BF), mean(spring$GC0AS), mean(spring$GC0BS))
#find what airT is at the median
#df[which(df$Amount == min(df$Amount)), ]
airtFA <- mean(fall$AirTF[which(fall$GC0AF == median(fall$GC0AF))])
airtFB <- mean(fall$AirTF[which(fall$GC0BF == median(fall$GC0BF))])
airtSA <- mean(spring$AirTS[which(spring$GC0AS == median(spring$GC0AS))])
airtSB <- mean(spring$AirTS[which(spring$GC0BS == median(spring$GC0BS))])

airT <- c(airtFA, airtFB, airtSA, airtSB)
ID <- c("FA", "FB", "SA", "SB")
#df of mean water T at GC head, mean airT when the median temp occurs, and the time ID
GC.means <- data.frame(means, airT, ID)

#add summer deployment to data
GC.summer <- filter(potet, site == "Glac")
airtsum <- mean(GC.summer$airT[which(GC.summer$temp.cor == GC.summer$med.headtemp)])

#do it again but with summer deployment added
means <- c(mean(fall$GC0AF), mean(fall$GC0BF), mean(spring$GC0AS), 
           mean(spring$GC0BS), GC.summer$avg.headtemp[1])
airT <- c(airtFA, airtFB, airtSA, airtSB, airtsum)
ID <- c("FallA", "FallB", "SpringA", "SpringB","Summer")
GC.means <- data.frame(means, airT, ID)

#plot them all
gc.fall2017 <- select(fall, temptime, AirTF, GC0AF)%>%
  rename(datetime = temptime, airT = AirTF, headT = GC0AF)%>%
  mutate(deployment = "Fall 2017")
gc.spring2017 <- select(spring, temptime, AirTS, GC0AS)%>%
  rename(datetime = temptime, airT = AirTS, headT = GC0AS)%>%
  mutate(deployment = "Spring 2017")
gc.summer2019 <- select(GC.summer, rnd.dates, airT, temp.cor)%>%
  rename(datetime = rnd.dates, headT = temp.cor)%>%
  mutate(deployment = "Summer 2019")


```

