---
title: "Figure set 10_3"
output:
  html_document: default
  pdf_document: default
---
10/4
Make plots with topo metrics, make final figure set to send to JP  

```{r global_options, include=FALSE}
#global settings
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

```{r}
#Packages
library(tidyverse)
library(lubridate)
library(ggridges)
```

```{r}
#I need to make a data sheet that has one sensor per site
#in order to pull of the plots I want to make
temps <- read.csv("Tempswithdmetrics10_3.csv")
topo <- read.csv("topodata 10_4.csv")

#format time and other stuff
temps$rnd.dates <- ymd_hms(temps$rnd.dates)
temps <- temps %>% mutate_each(list(as.factor), sensor)
temps <- temps %>% mutate_each(list(as.character), site, type, shed)

temps.water <- filter(temps, type != "air")

temps.water <- filter(temps.water, site %in% c("ULB2HA", "ULB2CB","ULB3HA", "ULB3CB", "ULB4HA", "ULB4CA", "RMO1HA", "RMO1CB", "RMO2HA", "RMO2CB", "RMO3HB", "RMO3CB","MUL2HA", "MUL2CB", "MUL4HB", "MUL4CA", "MUL7HB", "MUL7CA","W600B", "W400A", "GC300B","GC100B", "LS180B", "LS0B"))

temps.water$site <- gsub('.{2}$', '', temps.water$site)

temps.water <- temps.water %>%
  mutate(type = replace(type, type == "channel", "Downstream"),
         type = replace(type, type == "head", "Head"),
         site = replace(site, site == "W60", "Wind"),
         site = replace(site, site == "W40", "Wind"),
         site = replace(site, site == "GC10", "Glac"),
         site = replace(site, site == "GC30", "Glac"),
         site = replace(site, site == "LS", "Land"),
         site = replace(site, site == "LS18", "Land"))

topo <- topo %>% mutate_each(list(as.character), Site, type, Shed)
topo <- topo %>% 
  select(Site, type, Slope..percent.rise., Elevation..ft., UAA..ft2.) %>% 
  rename(site = Site)
topo <- topo %>%
  mutate(type = replace(type, type == "Down", "Downstream"),
         type = replace(type, type == "head", "Head"),
         site = replace(site, site == "W600", "Wind"),
         site = replace(site, site == "W400", "Wind"),
         site = replace(site, site == "GC100", "Glac"),
         site = replace(site, site == "GC300", "Glac"),
         site = replace(site, site == "LS0", "Land"),
         site = replace(site, site == "LS180", "Land"))
#selecting sites, renaming one of the columns in the same function

#combine the datasets by Site and type
comb <- left_join(temps.water, topo, by = c("site", "type"))
```

Plot time  
Temperatures vary with Elevation  
```{r}
#making plots
#Elevation vs distribution
elevators <- ggplot(data = comb, 
                    aes(x = fct_reorder(site, Elevation..ft.),
                        y = Value,
                        fill = type))+
  theme_classic()+
  labs(x = "Elevation",
       y = "WaterT (C)")+
  geom_boxplot()+
  facet_grid(rows = vars(type))
elevators

elevator.ridge <- ggplot(data = comb,
                         aes(x = Value,
                             y = fct_reorder(site, Elevation..ft.),
                             fill = type))+
  geom_density_ridges2(mapping = aes(scale=1))+
  theme_classic()+
  theme(axis.title.y= element_blank(),
        axis.title.x=element_text(size = 17),
        axis.ticks.y=element_blank(),
        strip.text.y = element_text(angle = 180, hjust = 1),
        line = element_blank(),
        axis.text.x = element_text(size = 17),
        axis.text.y = element_text(size = 17))+
  scale_y_discrete(expand = c(0.001, 0))+
  scale_x_continuous(limits = c(8,20), expand = c(0.001, 0))+
  xlab("Temp (C)")
elevators
elevator.ridge
```

Air temp plots  

```{r}
#Before I can plot airT stuff I need to get some kind of AirT data into my df
#comine datasets by time and shed
temps.air <- filter(temps, type == "air")

temps.air <- temps.air %>% mutate_each(list(as.character), site, type, shed)
temps.air <- temps.air %>% 
  select(shed, Value, rnd.dates, d.mean, d.min, d.max, d.sd) %>% 
  rename(airT = Value, air.d.mean = d.mean, air.d.min = d.min, air.d.max = d.max, air.d.sd = d.sd)

#brush is the new master datasheet
brush <- left_join(comb, temps.air, by = c("shed", "rnd.dates"))

#making summary df
presump <- brush %>% select(-X, -sensor, -shed, -day, -numb, -A.B, -rnd.dates)
shed.presump <- brush %>% select(site, shed) %>% distinct()

sump <- presump %>% group_by(site, type) %>% summarise_each(list(mean))

sump <- left_join(sump, shed.presump, by = c("site"))
```
As drainage area increases, average waterT increases  
```{r}
#plots with sump
#plotting uaa vs avg water T
drain.d <- filter(sump, type )

drain <- ggplot(sump, aes(x = UAA..ft2.,
                           y = Value,
                           color = shed,
                           ))+
  geom_point(aes(shape = type), size = 4)+
  geom_smooth(method = 'lm', se = FALSE)+
  theme_classic()+
  scale_color_brewer(palette = "Dark2")+
  labs(x = "Drainage Area (ft^2)",
       y = "Average WaterT (C)")
drain
```
Slope has some kind of control on waterT  
```{r}
#plotting slope vs avg water T
steep <- ggplot(sump, aes(x = Slope..percent.rise.,
                          y = Value,
                          color = shed))+
  geom_point(aes(shape = type), size = 4)+
  geom_smooth(method = 'lm', se = FALSE)+
  theme_classic()+
  scale_color_brewer(palette = "Dark2")+
  labs(x = "Slope (%)",
       y = "Average WaterT (C)")
steep
```
Water temperatures at downstream sites vary with AirT, but water temperatures at head sites do not vary with AirT  
```{r}
#airT vs WaterT
brush.h <- filter(brush, type == "Head")
heady <- ggplot(brush.h, aes(x = airT,
                          y = Value,
                          color = shed))+
  geom_point(size = 1,
             alpha = 0.25)+
  #geom_smooth(method = 'lm', se = FALSE)+
  theme_classic()+
  scale_color_brewer(palette = "Dark2")+
  labs(x = "Average airT (C)",
       y = "Average WaterT (C)",
       title = "Head sites")

#downstream sites
brush.d <- filter(brush, type == "Downstream")
downy <- ggplot(brush.d, aes(x = airT,
                          y = Value,
                          color = shed))+
  geom_point(size = 1,
             alpha = 0.25)+
  #geom_smooth(method = 'lm', se = FALSE)+
  theme_classic()+
  scale_color_brewer(palette = "Dark2")+
  labs(x = "Average airT (C)",
       y = "Average WaterT (C)",
       title = "Downstream sites")

downy
heady
```

Make new plots that I talked about with JP
```{r}
trug <- ggplot(comb, 
               aes(x = Elevation..ft.,
                   y = Value,
                   group = site))+
  geom_boxplot(aes(fill = type)
                   )+
  theme_classic()+
  labs(x = "Elevation",
       y = "WaterT (C)")
  #scale_x_continuous()+
  
trug

#group = cut_interval(Elevation..ft., length = 1))

ggplot(data = NDVI_ts, aes(x = date, y = NDVI)) +
  geom_boxplot(aes(fill = interaction(Trial.group, Treatment),
                   group = interaction(factor(date), Trial.group, Treatment))) + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_date(breaks = "1 week", labels = date_format("%d-%b")) +
  scale_fill_manual(name = "Treatment",
                    values = c("#FEE0D2", "#DE2D26", "#DEEBF7", "#3182BD"))
```

10/24- Going to stop banging my head against the wall about the boxplot issue, try to get some of the other plots put together

use average slope and average elevation to make plots- need to combine the data sheets i made
```{r}
#reading in data sheets within the folder
mose <- read.csv("shed data 10_11/shed data 10_11/moselevstats.csv", header = T, sep = ",")
mule <- read.csv("shed data 10_11/shed data 10_11/mulelevstats.csv", header = T, sep = ",")
ids <- read.csv("shed data 10_11/shed data 10_11/slopeids.csv", header = T, sep = ",")
stats <- read.csv("shed data 10_11/shed data 10_11/slopestats.csv", header = T, sep = ",")
ulbe <- read.csv("shed data 10_11/shed data 10_11/ulbelevstats.csv", header = T, sep = ",")

#combine the data sets
#format the "master" sheet- ids
ids <- select(ids, Site, type, pour_ord)
stats <- select(stats, -OBJECTID, -COUNT, -RANGE, -SUM, -AREA)%>% 
  rename(pour_ord = VALUE)
mose <- select(mose, -OBJECTID, -COUNT,  -RANGE, -SUM)%>%
  rename(pour_ord = VALUE)
mule <- select(mule, -OBJECTID, -COUNT,  -RANGE, -SUM)%>%
  rename(pour_ord = VALUE)
ulbe <- select(ulbe, -OBJECTID, -COUNT,  -RANGE, -SUM)%>%
  rename(pour_ord = VALUE)

#make new frame with all of the new data
bug <- left_join(ids, stats, by = "pour_ord")%>%
  rename(slope.min = MIN, slope.max = MAX, slope.mean = MEAN, slope.sd = STD)%>%
  mutate_each(list(as.character), Site, type)%>%
  mutate(type = replace(type, type == "Down", "Downstream"))

gut <- bind_rows(mose, mule, ulbe)
buggy <- left_join(bug, gut, by = "pour_ord")%>%
  rename(elev.min = MIN, elev.max = MAX, elev.mean = MEAN, elev.sd = STD)

#changed the name of GG sites
buggy <- buggy %>%
  mutate(Site = replace(Site, Site == "W600", "Wind"),
         Site = replace(Site, Site == "W400", "Wind"),
         Site = replace(Site, Site == "GC100", "Glac"),
         Site = replace(Site, Site == "GC300", "Glac"),
         Site = replace(Site, Site == "LS0", "Land"),
         Site = replace(Site, Site == "LS180", "Land"
         ))

#add new frame with topo metrics to master data frame from before
crat <- select(comb, -X, -sensor, -numb, -day)%>%
  rename(Site = site)
buggy <- buggy %>% mutate_each(list(as.character), Site, type)
crater <- inner_join(crat, buggy, by = c("Site", "type"))
```

Crater is the one- time to make some sick plots based off of it
```{r}
#Mean T vs size/elev
crater <- mutate(crater, size.elev = AREA/elev.mean, elev.size = elev.mean/AREA)

gronk1 <- ggplot(crater, aes(y = d.mean,
                             x = size.elev,
                             color = shed,
                             shape = type))+
  geom_point(aes(),
                 size = 2)+
  geom_smooth(method = 'lm', se = FALSE)+
  theme_classic()+
  scale_color_brewer(palette = "Dark2")+
    facet_grid(cols = vars(type))+

  xlab("area(ft2) / avg elev (ft)")
gronk1

gronk2 <- ggplot(crater, aes(y = d.mean,
                             x = elev.mean,
                             color = shed,
                             shape = type))+
  geom_point(aes(),
                 size = 2)+
  geom_smooth(method = 'lm', se = FALSE)+
  theme_classic()+
  scale_color_brewer(palette = "Dark2")+
    facet_grid(cols = vars(type))+

  xlab("avg elev (ft)")
gronk2

gronk3 <- ggplot(crater, aes(y = d.mean,
                             x = AREA,
                             color = shed,
                             shape = type))+
  geom_point(aes(),
                 size = 2)+
  geom_smooth(method = 'lm', se = FALSE)+
  theme_classic()+
  scale_color_brewer(palette = "Dark2")+
    facet_grid(cols = vars(type))+

  xlab("area(ft2)")
gronk3
```

```{r}
gronk4 <- ggplot(crater, aes(y = d.sd,
                             x = size.elev,
                             color = shed,
                             shape = type))+
  geom_point(size = 2)+
  theme_classic()+
  facet_grid(cols = vars(type))+
  scale_color_brewer(palette = "Dark2")+
  geom_smooth(method = 'lm', se = FALSE)+
  xlab("area(ft2) / avg elev (ft)")
gronk4

gronk5 <- ggplot(crater, aes(y = d.sd,
                             x = AREA,
                             color = shed,
                             shape = type))+
  geom_point(aes(),
                 size = 2)+
  geom_smooth(method = 'lm', se = FALSE)+
    facet_grid(cols = vars(type))+

  theme_classic()+
  scale_color_brewer(palette = "Dark2")+
  xlab("area(ft2)")
gronk5

gronk6 <- ggplot(crater, aes(y = d.sd,
                             x = elev.mean,
                             color = shed,
                             shape = type))+
  geom_point(aes(),
                 size = 2)+
    facet_grid(cols = vars(type))+

  geom_smooth(method = 'lm', se = FALSE)+
  theme_classic()+
  scale_color_brewer(palette = "Dark2")+
  xlab("Elevation(ft)")
gronk6
```

```{r}
#are downstream sites more related to heads or elev, slope, uaa?
d.crater <- filter(crater, type == "Downstream")

#plot down vs heads
#need new data sheet that has the head temp as a variable for each down observation
#join two filtered data sets
di <- filter(crater, type == "Downstream")%>%
  select(Site, shed, type, Value, rnd.dates, d.mean, d.sd)%>%
  rename(down.temp = Value, down.dmean = d.mean, down.dsd = d.sd)
         #slope.mean, slope.sd, AREA, elev.mean)
ll <- filter(crater, type == "Head")%>%
  select(Site, Value, shed, rnd.dates, d.mean, d.sd)%>%
  rename(head.temp = Value, head.dmean = d.mean, head.dsd = d.sd)
dill <- left_join(di, ll, by = c("Site", "rnd.dates","shed"))
#success, plot time
down.heads <- ggplot(dill, aes(x = head.temp,
                                   y = down.temp,
                                   color = shed))+
  stat_density2d(size = 0.5)+
  scale_color_brewer(palette = "Dark2")+
  #geom_point(size = 2)+
  theme_classic()
down.heads

davg.down.heads <- ggplot(dill, aes(x = head.dmean,
                                    y = down.dmean,
                                    color = shed))+
  stat_density2d(size = 0.5)+
  scale_color_brewer(palette = "Dark2")+
  theme_classic()
davg.down.heads

dsd.down.heads <- ggplot(dill, aes(x = head.dsd,
                                   y = down.dsd,
                                   color = shed))+
  stat_density2d(size = 0.5)+
  scale_color_brewer(palette = "Dark2")+
  theme_classic()
dsd.down.heads
#plot down vs elev

#plot down vs slope

#plot down vs uaa
```

```{r}
#plot down vs elev
del <- ggplot(d.crater, aes(x = elev.mean,
                            y = d.mean))+
  geom_point(aes(color = shed), size = 2)+
  geom_smooth(aes(color = shed), method = 'lm', se = FALSE)+
  geom_smooth(method = 'lm', se = FALSE)+
  scale_color_brewer(palette = "Dark2")+
  theme_classic()
del

del2 <- ggplot(d.crater, aes(x = elev.mean,
                            y = d.sd))+
  geom_point(aes(color = shed), size = 2)+
  geom_smooth(aes(color = shed), method = 'lm', se = FALSE)+
  geom_smooth(method = 'lm', se = FALSE)+
  scale_color_brewer(palette = "Dark2")+
  theme_classic()
del2

del.min <- ggplot(d.crater, aes(x = elev.mean,
                                y = d.min))+
  geom_point(aes(color = shed), size = 2)+
    geom_point(aes(color = shed), size = 2)+
  geom_smooth(aes(color = shed), method = 'lm', se = FALSE)+
  geom_smooth(method = 'lm', se = FALSE)+
  scale_color_brewer(palette = "Dark2")+
  theme_classic()
del.min
```

```{r}
#plot down vs slope
slo <- ggplot(d.crater, aes(x = slope.mean,
                            y = d.mean))+
  geom_point(aes(color = shed), size = 2)+
  geom_smooth(aes(color = shed), method = 'lm', se = FALSE)+
  geom_smooth(method = 'lm', se = FALSE)+
  scale_color_brewer(palette = "Dark2")+
  theme_classic()
slo

slo2 <- ggplot(d.crater, aes(x = slope.mean,
                            y = Value))+
  geom_point(aes(color = shed), size = 2)+
  geom_smooth(aes(color = shed), method = 'lm', se = FALSE)+
  geom_smooth(method = 'lm', se = FALSE)+
  scale_color_brewer(palette = "Dark2")+
  theme_classic()
slo2
```

```{r}
#plot down vs UAA
ua <- ggplot(d.crater, aes(x = slope.mean,
                            y = Value))+
  geom_point(aes(color = shed), size = 2)+
  geom_smooth(aes(color = shed), method = 'lm', se = FALSE)+
  geom_smooth(method = 'lm', se = FALSE)+
  scale_color_brewer(palette = "Dark2")+
  theme_classic()
ua
```

Make plots with just heads from those above












How to make plots with just one point for all of the temperatures for each stream? 

If I divide the waterT by AirT, and AirT is the greatest control, then it should be some unitless number representing the temperature of the water without the influence of the air

```{r}
#average of the T normalized by air temperature- use to make one point
#need to make new df that includes the air temp of each site as a variable
temps.air <- filter(temps, type == "air")%>%
  select(shed, Value, rnd.dates, d.mean)%>%
  rename(air.t = Value, air.d.mean = d.mean)

norm <- left_join(crater, temps.air, by = c("shed", "rnd.dates"))%>%
  mutate(wt.airt = Value/air.t, wt.airt.dmean = d.mean/air.d.mean)

chunk <- norm%>%
  group_by(Site, type)%>%
  summarise(avg.wtairt = mean(wt.airt, na.rm = TRUE), 
            avg.Value = mean(Value), 
            avg.wtairtdmean = mean(wt.airt.dmean, na.rm = TRUE))

grut <- crater%>%
  select(Site, type, shed, UAA..ft2., slope.mean, elev.mean, size.elev)


grup <- inner_join(grut, unique(chunk), by = c("Site", "type"))%>%
  distinct()
#data sheet that has the normalized temps and other metrics of interest
#time to plot them
```

```{r}
#using df grup, which has topo metrics and the normalized temps
grup.down <- filter(grup, type == "Downstream")
grup.head <- filter(grup, type == "Head")

grup1 <- ggplot(grup, aes(x = elev.mean,
                          y = avg.wtairt,
                          color = shed))+
  geom_point(aes(shape = type), size = 2)+
  geom_smooth(aes(color = shed), method = 'lm', se = FALSE)+
  theme_classic()+
  facet_grid(cols = vars(type))
  scale_color_brewer(palette = "Dark2")
grup1
```

calculate rates, plot against everything
```{r}
#calculate derivative of lines
rat <- crater%>%
  select(Site, type, Value, rnd.dates)%>%
  mutate(value.1 = lag(Value))%>%
  mutate(rate = value.1 - Value)
```

```{r}
#calculate the rate of warming moving downstream
#read in csv with straight line distance between head and downstream site
dist <- read.csv("distances 11_1.csv")
dist <- dist %>% mutate_each(list(as.character), Site)

warm <- dill%>%
  left_join(dist, by = "Site")%>%
  mutate(diff = down.temp - head.temp)%>%
  mutate(rate = diff / straight.line.Dist.to.head.m)

rat.time <- ggplot(warm, aes(x = rnd.dates,
                             y = rate))+
  geom_line(aes(color = Site))+
  theme_classic()
rat.time

#calculate warming rate from JUNE 27 onward
filter(FL_DATE >= as.Date("2014-01-05"))
```

```{r}
#rate vs slope, elev, uaa
willy <- select(warm, Site, rnd.dates, rate)
#df with topographic metrics, temp stuff, and rates
will <- left_join(crater, willy, by = "Site", "rnd.dates")
```

11/5
Need to make final figure set to show JP and Christa for Friday
-dont do anything with rates until I can calculate the distance along the lines between the two points

```{r}
#plot down vs heads
#need new data sheet that has the head temp as a variable for each down observation
#join two filtered data sets
di <- filter(crater, type == "Downstream")%>%
  select(Site, shed, type, Value, rnd.dates, d.mean, d.sd)%>%
  rename(down.temp = Value, down.dmean = d.mean, down.dsd = d.sd)
         #slope.mean, slope.sd, AREA, elev.mean)
ll <- filter(crater, type == "Head")%>%
  select(Site, Value, shed, rnd.dates, d.mean, d.sd)%>%
  rename(head.temp = Value, head.dmean = d.mean, head.dsd = d.sd)
dill <- left_join(di, ll, by = c("Site", "rnd.dates","shed"))
#success, plot time
down.heads <- ggplot(dill, aes(x = head.temp,
                               y = down.temp))+
  stat_density2d(aes(color = shed),
                 size = 0.5)+
   geom_smooth(method = 'lm', se = FALSE)+
  scale_color_brewer(palette = "Dark2")+
  #geom_point(size = 2)+
  theme_classic()
down.heads
```


```{r}
davg.down.heads <- ggplot(dill, aes(x = head.dmean,
                                    y = down.dmean))+
   stat_density2d(aes(color = shed),
                 size = 0.5)+
   geom_smooth(method = 'lm', se = FALSE)+
  scale_color_brewer(palette = "Dark2")+
  theme_classic()
davg.down.heads

d.crater.dill <- left_join(d.crater, ll, by = c("Site", "rnd.dates","shed"))

d.mean.model <- lm(Value ~  head.temp + slope.mean + elev.mean  + UAA..ft2., data = d.crater.dill)
summary(d.mean.model)

h.mean.model <- lm(head.temp ~ slope.mean  + elev.mean + AREA + UAA..ft2., data = d.crater.dill)
summary(h.mean.model)

head.form <- 1.291e-01 * slope.mean + 
  -6.921e-04 * elev.mean + 
   3.296e-07 * AREA +
   3.025e-06 * UAA..ft2.+
   8.294e+00

modtest <- d.crater.dill%>%
  select(Site, shed, rnd.dates, slope.mean, elev.mean, AREA, UAA..ft2., head.temp)

detach(modtest)
modtestdf <- left_join(d.crater.dill)

#make a data frame to use to test the model equation
modeltester <- d.crater.dill%>%
  select(Site, shed, slope.mean, elev.mean, AREA, UAA..ft2., head.temp)%>%
  mutate(model = 1.291e-01 * slope.mean + 
  -6.921e-04 * elev.mean + 
   3.296e-07 * AREA +
   3.025e-06 * UAA..ft2.+
   8.294e+00)%>%
  group_by(Site)%>%
  mutate(avg.head = mean(head.temp, na.rm = TRUE))

modeltester <- select(modeltester, -head.temp)
modeltester <- unique(modeltester)
modeltester <- modeltester%>%
  mutate(diff = avg.head - model)%>%
  mutate(diff.2 = sqrt(diff * diff))

testmodel <- ggplot(modeltester, aes(x = elev.mean,
                                     y = diff.2,
                                     color = shed))+
  geom_point(size = 2)+
  theme_classic()
testmodel
```

```{r}
#make data sheet to save and use for plotting on the newer figure set
#brush- has air temp stuff
#crater- everything else
brushed <- brush%>%
  select(site, shed, rnd.dates, airT, air.d.mean, air.d.min, air.d.max, air.d.sd)%>%
  rename(Site = site)


dogg <- left_join(d.crater.dill, brushed, by = c("Site", "shed", "rnd.dates"))

#write.csv(dogg, file = "Tempsanddata_8_11.csv")
#write.csv(warm, file = "straightlinerates11_8.csv")
```

