---
title: "Figure set 11_8"
output: html_document
---

```{r global_options, include=FALSE}
#global settings
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

```{r}
#Packages
library(tidyverse)
library(lubridate)
library(ggridges)
```

```{r}
#read in data set
dogg <- read.csv("Tempsanddata_11_8.csv")
warm <- read.csv("straightlinerates11_8.csv")

warm <- select(warm, Site, shed, rnd.dates, straight.line.Dist.to.head.m, diff, rate)

dogg <- left_join(dogg, warm, by = c("Site", "shed", "rnd.dates"))

#adding averages
chunk <- dogg%>%
  group_by(Site, type)%>%
  summarise(avg.headtemp = mean(head.temp, na.rm = TRUE), 
            avg.Value = mean(Value))

doge <- inner_join(dogg, unique(chunk), by = c("Site", "type"))%>%
  distinct()
```
  
Figures to be made- box and whisker plot of temp distributions and ranges of rates
```{r}
#boxplot of the temps by elevation
elevators <- ggplot(data = dogg, 
                    aes(x = fct_reorder(ite, Elevation..ft.),
                        y = Value,
                        fill = type))+
  theme_classic()+
  labs(x = "Elevation",
       y = "WaterT (C)")+
  geom_boxplot()+
  facet_grid(rows = vars(type))+
  theme(strip.background = element_blank(),
        strip.text = element_blank())
elevators
```
```{r}
#rates
rate.box <- ggplot(data = dogg, 
                    aes(x = fct_reorder(Site, Elevation..ft.),
                        y = rate))+
  theme_classic()+
  labs(x = "Elevation",
       y = "WaterT (C)")+
  geom_boxplot()+
  facet_grid(rows = vars(type))+
  theme(strip.background = element_blank(),
        strip.text = element_blank())
rate.box
```

```{r}
#warming rates since June 27- period of continuous warming

```

```{r}
#results of the multi-linear model
h.mean.model <- lm(head.temp ~ slope.mean  + elev.mean + UAA..ft2. + air.d.mean, data = dogg)
summary(h.mean.model)

h.model <- lm(head.temp ~ slope.mean  + elev.mean + UAA..ft2., data = dogg)
summary(h.model)
```
```{r}
#make a data frame to use to test the model equation
modeltester <- dogg%>%
  select(Site, shed, slope.mean, elev.mean, elev.size, UAA..ft2., head.temp)%>%
  mutate(model = 1.285e-01 * slope.mean + 
  -6.103e-04 * elev.mean + 
   -1.062e+01 * elev.size +
   1.585e-06 * UAA..ft2.+
   8.458e+00)%>%
  group_by(Site)%>%
  mutate(avg.head = mean(head.temp, na.rm = TRUE))

modeltester <- select(modeltester, -head.temp)
modeltester <- unique(modeltester)
modeltester <- modeltester%>%
  mutate(diff = avg.head - model)%>%
  mutate(diff.2 = sqrt(diff * diff))

testmodel <- ggplot(modeltester, aes(x = avg.headtemp,
                                     y = model,
                                     color = shed))+
  geom_point(size = 2)+
  theme_classic()
testmodel
```


Make plot of the accuracy of the linear model

```{r}
#slope vs avg temps
#plot down vs slope
slo <- ggplot(doge, aes(x = slope.mean,
                            y = avg.headtemp))+
  geom_point(aes(color = shed), size = 2)+
  geom_smooth(aes(color = shed), method = 'lm', se = FALSE)+
  scale_color_brewer(palette = "Dark2")+
  theme_classic()
slo

slo2 <- ggplot(doge, aes(x = slope.mean,
                            y = avg.Value))+
  geom_point(aes(color = shed), size = 2)+
  geom_smooth(aes(color = shed), method = 'lm', se = FALSE)+
  scale_color_brewer(palette = "Dark2")+
  theme_classic()
slo2
```

```{r}
#elevation vs temps
del <- ggplot(doge, aes(x = elev.mean,
                            y = avg.headtemp))+
  geom_point(aes(color = shed), size = 2)+
  geom_smooth(aes(color = shed), method = 'lm', se = FALSE)+
  geom_smooth(method = 'lm', se = FALSE)+
  scale_color_brewer(palette = "Dark2")+
  theme_classic()
del

del2 <- ggplot(doge, aes(x = elev.mean,
                            y = avg.Value))+
  geom_point(aes(color = shed), size = 2)+
  geom_smooth(aes(color = shed), method = 'lm', se = FALSE)+
  geom_smooth(method = 'lm', se = FALSE)+
  scale_color_brewer(palette = "Dark2")+
  theme_classic()
del2
```

```{r}
#head temps vs down temps
down.heads <- ggplot(dogg, aes(x = head.temp,
                               y = Value,
                                   color = shed))+
  stat_density2d(size = 0.5)+
  scale_color_brewer(palette = "Dark2")+
  #geom_point(size = 2)+
  theme_classic()
down.heads
```

Making plots of regression results vs actual temperatures
```{r}
#results of the multi-linear model
h.model <- lm(head.temp ~ 
                slope.mean  +
                elev.mean + 
                UAA..ft2.,data = dogg)

h.model.air <- lm(head.temp ~ 
                    slope.mean  + 
                    elev.mean + 
                    UAA..ft2. + 
                    air.d.mean, data = dogg)

d.model <- lm(Value ~ 
                slope.mean  + 
                elev.mean + 
                UAA..ft2. , data = dogg)

d.model.air <- lm(Value ~ 
                    slope.mean  + 
                    elev.mean + 
                    UAA..ft2. + 
                    air.d.mean, data = dogg)

h.avg.model <- lm(head.dmean ~ 
                slope.mean  +
                elev.mean + 
                UAA..ft2.,data = dogg)
summary(h.avg.model)
hair.avg.model <- lm(head.dmean ~ 
                slope.mean  +
                elev.mean + 
                UAA..ft2. +
                air.d.mean  ,data = dogg)
summary(hair.avg.model)


#run regression for just moses creek measured values and see if it is a better predictor than using all of the measurements
moses.dogg <- filter(dogg, shed == "RMO")
#run lm
mos.h.avg.model <- lm(head.dmean ~
                        slope.mean +
                        elev.mean +
                        UAA..ft2., data = moses.dogg)

modeltester <- dogg%>%
  select(Site, shed, slope.mean, elev.mean, AREA, UAA..ft2., head.temp)%>%
  mutate(h.avg.model = 1.261e-01 * slope.mean + 
  -6.722e-04 * elev.mean + 
   5.125e-06 * UAA..ft2.+
   8.329e+00)%>%
  group_by(Site)%>%
  mutate(avg.head = mean(head.temp, na.rm = TRUE))
#using the model results for moses in this plot
moss <- read.csv("modelmaybemoses_11_21.csv")

plotJPwants <- ggplot()+
  theme_classic()+
  geom_point(data = modeltester, aes(x = avg.head,
                              y = h.avg.model,
                              color = shed), size = 3)+
  geom_point(data = moss, aes(x = h.avg.model,
                              y = h.avg.model))+
   #geom_smooth(method = 'lm', se = FALSE)+
  labs(x = "Measured average head temp (C)",
       y = "Modeled average head temp")
plotJPwants
```

11/9
Making a first crack at the insane idea Christa had to try to see over what timescale air temperature might matter using linear regressions

DAPR - Number of days included in the multiday precipitation total (MDPR)
SNOW - Snowfall
TMAX - Maximum temperature
TMIN - Minimum temperature
PRCP - Precipitation
TOBS - Temperature at the time of observation
MDPR - Multiday precipitation total (use with DAPR and DWPR, if available)
SNWD - Snow depth
```{r}
#read in data set of 100 years of cullowhee weather data- hell yeah
cull <- read.csv("Cullowheerain.csv")
cull$DATE <- ymd(cull$DATE)
cull$year <- year(cull$DATE)

ggplot(cull, aes(x = year))+
  geom_bar(aes(y = PRCP), stat = "identity")+
  geom_bar(aes(y = SNOW), stat = "identity", color = "blue")+
  theme_classic()
#make df with the last 20 years in the record
last20 <- filter(cull, year > 2000)
ggplot(last20, aes(x = DATE,
                   y = PRCP))+
  geom_line()+
  theme_classic()

last5 <- filter(cull, year > 2014)%>%
  select(-STATION, -DAPR, -MDPR, -SNWD)
```

Need the topographic metrics for GG
```{r}
#making df with topo metrics for GG sites
grib <- filter(dogg, shed == "GG")%>%
  select(Site, head.dmean, rnd.dates, slope.mean, UAA..ft2., elev.mean, air.d.mean)
#datasheet for JP
JP <- filter(dogg, shed == "GG")%>%
  select(Site, Value, d.mean, head.temp, head.dmean, rnd.dates, slope.mean, UAA..ft2., elev.mean, air.d.mean, rate)%>%
  rename(down.temp = Value, down.dmean = d.mean, warm.rate.c_m = rate)

JP <- mutate(JP, UAA.m2 = UAA..ft2.* 0.3048 *0.3048, elev.mean.m = elev.mean * 0.3048)%>%
  select(-UAA..ft2., -elev.mean)
#write.csv(JP, file = "GGheadtempdata_11_11.csv")


#formatting time
grib$rnd.dates <- ymd_hms(grib$rnd.dates)
#grib$rnd.dates <- date(grib$rnd.dates)

grib.base <- lm(head.dmean ~ slope.mean + UAA..ft2.  + air.d.mean, data = grib)
summary(grib.base)

grib.base.noair <- lm(head.dmean ~ slope.mean + UAA..ft2. + elev.mean, data = grib)
summary(grib.base.noair)

dd <- ddays(25)
```

```{r}
#running regressions
#grib
#last5
custom_stat_fun_2 <- function(x, na.rm = TRUE) {
    # x     = numeric vector
    # na.rm = boolean, whether or not to remove NA's
    
    m  <- mean(x, na.rm = na.rm)
    s  <- sd(x, na.rm = na.rm)
    hi <- m + 2*s
    lo <- m - 2*s
    
    ret <- c(mean = m, stdev = s, hi.95 = hi, lo.95 = lo) 
    return(ret)
}
shooty <- function(x, na.rm = TRUE){
  lm(head.dmean ~ gg.air + slope.mean + UAA..ft2., data = x)
}
#add topo metrics to the df
#make 3 duplicate data frames, one for each stream in GG, then append them to each other and use that in the for loop
last20$slope.mean <- grib$slope.mean[1]
last20$UAA..ft2. <- grib$UAA..ft2.[1]
last20$elev.mean <- grib$elev.mean[1]
#data frame for results of for loop regression
rdata <- data.frame()

for(i in 1:length(last20$DATE)){
  l <- 25*(i-1) + 1
  u <- 25*i
  dummy <- last20[l:u,]
  hap <- lm(head.dmean ~ gg.air + slope.mean + UAA..ft2., data = dummy)
  sum <- summary(hap)
  #output
  #column with the date
  rdata$date <- last20$DATE
  #r squared value from summary table
  rdata$r2 <- sum$r.squared
  #
  if(i == 1)alldat <- rdata                 
  if(i > 1)alldat <- rbind(alldat, rdata)
}

my_lms <- lapply(1:2, function(x) lm(grib$head.dmean ~ last5$TOBS + grib$slope.mean + grib$UAA..ft2.))

sapply(summaries, function(x) c(r_sq = x$r.squared, 
                                adj_r_sq = x$adj.r.squared))
```

11/13
Attempting to apply the model to the supposed channel heads in moses creek
```{r}
#reading in topo metrics from dem identified channel heads
UAA <- read.csv("outputs/UAA.csv")
elev <- read.csv("outputs/elev.csv")
slope <- read.csv("outputs/slope.csv")
ids <- read.csv("ids2.csv")
#remove 83, 69, 59, 34, 26, 17, 16, 14, 7, 3
UAA <- filter(UAA, MEAN > 3)

ids$Site <- ids$pour_ord
slope <- select(slope, OBJECTID, MEAN)%>%
  rename(Site = OBJECTID, slope.mean = MEAN)
elev <- select(elev, OBJECTID, MEAN)%>%
  rename(Site = OBJECTID, elev.mean = MEAN)
UAA <- select(UAA, OBJECTID, AREA)%>%
  rename(Site = OBJECTID, uaaft2 = AREA)

mosay <- inner_join(UAA, slope, by = "Site")
chief <- inner_join(mosay, elev, by = "Site")

ggplot()+
  geom_boxplot(data = chief, aes(y = uaaft2))+
  theme_classic()
```

```{r}
#boxplots to look at model moses data to see if I am smoking crack
ggplot(data = dogg)+
  geom_boxplot(aes(x = ))
```


```{r}
#apply the model to the hypothetical sites
#head avg temp model
mostest <- chief%>%
  mutate(h.avg.model = 1.261e-01 * slope.mean + 
  -6.722e-04 * elev.mean + 
   5.125e-06 * uaaft2+
   8.329e+00)

modelmaybemose <- left_join(ids, mostest, by = "Site")%>%
  select(Site, NEAR_X, NEAR_Y, h.avg.model)

mop <- modelmaybemose[complete.cases(modelmaybemose),]
#write.csv(mop, file = "modelmaybemoses_11_21.csv")

#to compare the model against the actual temps I need to use mostest
xarxes <- select(modeltester, -head.temp)
xarxes <- unique(xarxes)
xarxes <- xarxes[-6,] #remove duplicate MUL2

```

11/14
Attempting to use new rolling packages
```{r}
library(tidyquant)
```

```{r}
#demo data
#trying to use tidyquant
order.by(order_by = )

seat <- as.zoo(log(UKDriverDeaths))
time(seat) <- as.yearmon(time(seat))
seat <- merge(y = seat, y1 = lag(seat, k = -1),
  y12 = lag(seat, k = -2), all = FALSE)

#UKDriverdeaths is a time series object in R
#going to try to play around with timeseries
#formatting wind to remove duplicate values
wind.ts <- filter(grib, Site == "Wind")
wind.ts$rnd.dates <- date(wind.ts$rnd.dates)
wind.ts <- unique(wind.ts)
#converting just wind temps to a timeseries object
wind <- ts(wind.ts$head.dmean)
windy <- as.zoo(wind)


## run a rolling regression with a 3-year time window
## (similar to a SARIMA(1,0,0)(1,0,0)_12 fitted by OLS)
rr <- rollapply(seat, width = 36,
  FUN = function(z) coef(lm(y ~ y1 + y12, data = as.data.frame(z))),
  by.column = FALSE, align = "right")
#this is a failed method


test <- grib1%>%
  select()%>%
  tq_mutate(
        select     = air.d.mean,
        mutate_fun = rollapply, 
        # rollapply args
        width      = 30,
        align      = "right",
        by.column  = TRUE,
        FUN        = mean,
        # FUN args
        na.rm      = TRUE
    )%>%
  select(value)

#getting topo metrics
gg.slope <- grib$slope.mean[1]
gg.UAA <- grib$UAA..ft2.[1]
gg.elev <- grib$elev.mean[1]
gg.headavg <- 11.989
#applying topo metrics to last 20 years of temp data
last20.reg <- select(last20, DATE, TMAX, TMIN, TOBS)%>%
  mutate(slope.mean = gg.slope, UAA..ft2. = gg.UAA, elev.mean = gg.elev,
         head.temp = gg.headavg)

#make function that runs the multilinear regression
# Custom function to return mean, sd, 95% conf interval

test <- function(x, y){
  t <- x + y
  return(t)
}

head.d.mean <- select(grib, -rnd.dates, -air.d.mean)
head.temp <- unique(head.d.mean)

#my custom function
rickroll <- function(x, na.rm = TRUE){
  roll <- x
  model <- lm(wind.ts$head.dmean ~  
                roll  + 
                wind.ts$slope.mean + 
                wind.ts$UAA..ft2. + 
                wind.ts$elev.mean)
  r <- summary(model)$r.squared
  return(r)
}
#my attempt to do a rolling calculation
#success!
#last 5 years
gribregulation <- last5%>%
  tq_mutate(select = TOBS,
            mutate_fun = rollapply,
            width = 26,
            align = "right",
            by.column = FALSE,
            FUN = rickroll)
  
  
  rollapply(last5, width = 26,
                     FUN = rickroll,
                     by.column = FALSE, align = "right")
  
z <- ggplot(gribregulation, aes(x = DATE,
                           y = value))+
  geom_line()+
  theme_classic()

z + geom_hline(yintercept = 0.7557, color = "red")+
  geom_hline(yintercept = 0.8973, color = "blue")
#last 20 years
gribregulation20 <- last20%>%
  tq_mutate(select = TOBS,
            mutate_fun = rollapply,
            width = 26,
            align = "right",
            by.column = FALSE,
            FUN = rickroll)
  
  
l <- ggplot(gribregulation20, aes(x = DATE,
                           y = value))+
  geom_point()+
  theme_classic()

l + geom_hline(yintercept = 0.7557, color = "red")+
  geom_hline(yintercept = 0.8973, color = "blue")
#entire record
gribregulation20 <- cull%>%
  tq_mutate(select = TOBS,
            mutate_fun = rollapply,
            width = 26,
            align = "right",
            by.column = FALSE,
            FUN = rickroll)
  
  
ggplot(cull, aes(x = DATE,
                           y = value))+
  geom_line()+
  theme_classic()
```
got some crazy error messages, I think there are problems with the factor levels- need to revisit with fresh eyes

```{r}
#wind regressions to compare to model results above
wind.noair <- lm(head.dmean ~ slope.mean + UAA..ft2. + elev.mean, data = wind.ts)
summary(wind.noair)
```
```{r}
#time period that correlates best with wind is
wind <- gribregulation[270:295,]
glac <- gl.reg[271:296,]
land <- ls.reg[271:296,]


#need to find a way to run the regression for all three of the sites at once- a combined r2 value

#starting with running the others individually
ls.ts <- filter(grib, Site == "Land")
ls.ts$rnd.dates <- date(ls.ts$rnd.dates)
ls.ts <- unique(ls.ts)

gl.ts <- filter(grib, Site == "Glac")
gl.ts$rnd.dates <- date(gl.ts$rnd.dates)
gl.ts <- unique(gl.ts)

#applying topo metrics to last 20 years of temp data
rickroll2 <- function(x, na.rm = TRUE){
  roll <- x
  model <- lm(gl.ts$head.dmean ~  
                roll  + 
                gl.ts$slope.mean + 
                gl.ts$UAA..ft2. + 
                gl.ts$elev.mean)
 
  r <- summary(model)$r.squared
  return(r)
}
#my attempt to do a rolling calculation
#success!
#last 5 years
gl.reg <- last5%>%
  tq_mutate(select = TOBS,
            mutate_fun = rollapply,
            width = 26,
            align = "right",
            by.column = FALSE,
            FUN = rickroll2)
  
glacier.regplot <- ggplot(gl.reg, aes(x = DATE,
                           y = value))+
  geom_line()+
  theme_classic()

glacier.regplot + geom_hline(yintercept = 0.7557, color = "red")+
  geom_hline(yintercept = 0.8973, color = "blue")
```

Landslide
```{r}
#starting with running the others individually
ls.ts <- filter(grib, Site == "Land")
ls.ts$rnd.dates <- date(ls.ts$rnd.dates)
ls.ts <- unique(ls.ts)
ls.ts <- ls.ts[-26,]

#applying topo metrics to last 20 years of temp data
rickroll3 <- function(x, na.rm = TRUE){
  roll <- x
  model <- lm(ls.ts$head.dmean ~  
                roll  + 
                ls.ts$slope.mean + 
                ls.ts$UAA..ft2. + 
                ls.ts$elev.mean)
 
  r <- summary(model)$r.squared
  return(r)
}
#my attempt to do a rolling calculation
#success!
#last 5 years
ls.reg <- last5%>%
  tq_mutate(select = TOBS,
            mutate_fun = rollapply,
            width = 26,
            align = "right",
            by.column = FALSE,
            FUN = rickroll3)
  
ls.regplot <- ggplot(ls.reg, aes(x = DATE,
                           y = value))+
  geom_line()+
  theme_classic()

ls.regplot + geom_hline(yintercept = 0.7557, color = "red")+
  geom_hline(yintercept = 0.8973, color = "blue")
```

Wind
```{r}
#starting with running the others individually
w.ts <- filter(grib, Site == "Wind")
w.ts$rnd.dates <- date(w.ts$rnd.dates)
w.ts <- unique(w.ts)
#w.ts <- ls.ts[-26,]

#applying topo metrics to last 20 years of temp data
rickroll4 <- function(x, na.rm = TRUE){
  roll <- x
  model <- lm(w.ts$head.dmean ~  
                roll  + 
                w.ts$slope.mean + 
                w.ts$UAA..ft2. + 
                w.ts$elev.mean)
 
  r <- summary(model)$r.squared
  return(r)
}
#my attempt to do a rolling calculation
#success!
#last 5 years
w.reg <- last5%>%
  tq_mutate(select = TOBS,
            mutate_fun = rollapply,
            width = 26,
            align = "right",
            by.column = FALSE,
            FUN = rickroll4)
  
ls.regplot <- ggplot(ls.reg, aes(x = DATE,
                           y = value))+
  geom_line()+
  theme_classic()

ls.regplot + geom_hline(yintercept = 0.7557, color = "red")+
  geom_hline(yintercept = 0.8973, color = "blue")
```

```{r}
library(gridExtra)

wind <- gribregulation[270:295,]
wind.back <- gribregulation[270:320,]
glac <- gl.reg[271:296,]
glac.back <- gl.reg[271:321,]
land <- ls.reg[271:296,]
land.back <- ls.reg[271:321,]

rain <- ggplot(wind.back, aes(x = DATE,
                 y = PRCP))+
  geom_bar(stat = "identity")+
  xlab("")+
  theme_classic()+
  theme(axis.text.x=element_blank())

manyrs <- ggplot()+
  geom_line(data = wind.back, mapping = aes(x = DATE,
                                            y = value),
            color = "firebrick")+
  geom_line(data = land.back, mapping = aes(x = DATE,
                                            y = value),
            color = "slateblue")+
  geom_line(data = glac.back, mapping = aes(x = DATE,
                                            y = value), 
            color = "seagreen")+
  theme_classic()+
  geom_hline(yintercept = 0.7557, color = "red")+
  geom_hline(yintercept = 0.8973, color = "blue")

  lay <- rbind(c(1),
             c(2),
             c(2))
grid.arrange(grobs = gs, layout_matrix = lay)


grid.arrange(rain, 
             manyrs, layout_matrix = lay)
```

Dotplot
```{r}
#combine the regression results of all three into a data frame
gr <- select(wind, DATE, value)%>%
  rename(wind = value)
oi <- select(land, DATE, value)%>%
  rename(land = value)
wn <- glac %>% rename(glac = value)

oiwn <- inner_join(wn, oi, by = "DATE")
groiwn <- inner_join(oiwn, gr, by = "DATE")
#plot of precip
rain <- ggplot(wind, aes(x = DATE,
                 y = PRCP))+
  geom_bar(stat = "identity")+
  xlab("")+
  theme_classic()+
  theme(axis.text.x=element_blank())

#restructure data 
groiwn2 <- groiwn %>%
  gather(key = "Site", value = "r2", c(glac, land, wind))

manyrs <- ggplot(data = groiwn2, aes(x = DATE))+
  geom_point(aes(y = r2, shape = Site))+
  theme_classic()+
  geom_hline(yintercept = 0.7557, color = "red")+
  geom_hline(yintercept = 0.8973, color = "blue")

  lay <- rbind(c(1),
             c(2),
             c(2))
grid.arrange(grobs = gs, layout_matrix = lay)


grid.arrange(rain, 
             manyrs, layout_matrix = lay)
```
  
  
Trying to add other two air temps to model to see if it improves
```{r}
#my custom function
rickroll7 <- function(x, na.rm = TRUE){
  roll <- x
  model <- lm(wind.ts$head.dmean ~  
                #roll$TOBS  +
                roll$TMAX +
                roll$TMIN +
                wind.ts$slope.mean + 
                wind.ts$UAA..ft2. + 
                wind.ts$elev.mean)
  r <- summary(model)$r.squared
  return(r)
}
#my attempt to do a rolling calculation
#success!
#last 5 years
gribregulation <- last5%>%
  tq_mutate(select = c(TMIN, TMAX),
                       #, TOBS),
            mutate_fun = rollapply,
            width = 26,
            align = "right",
            by.column = FALSE,
            FUN = rickroll)

test <- ggplot(gribregulation, aes(x = DATE,
                           y = value))+
  geom_line()+
  theme_classic()+
  labs(title = "Wind with TMIN and TMAX")

test + geom_hline(yintercept = 0.7557, color = "red")+
  geom_hline(yintercept = 0.8973, color = "blue")
```



  REading in new ICP data from Christa!!!

```{r}
elm <- read.csv("ICP results.csv")

elm <- filter(elm, type == "samp")%>%
  select(-No., -Name)%>%
  gather("element", "measurement", -type, -shed, -site, -date, Sodium, Ammonium, Potassium, Magnesium, Calcium, Fluoride, Chloride, Bromide, Nitrate, Sulfate)%>%
    mutate(measurement = replace(measurement, measurement == "n.a.", NA))%>%  
    mutate_each(list(as.double), measurement)%>% 
    mutate_each(list(as.character), site, type, shed)
elm$date <- mdy(elm$date)

ggplot(elm, aes(x = element,
                y = site))+
  geom_tile(aes(fill = measurement))+
   scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) +
  theme(legend.position = "none", 
        axis.ticks = element_blank(), 
        axis.text.x = element_text(size=12, 
                                   angle=90, hjust=0, colour="black"),
        axis.text.y = element_text(size=12, 
                                   angle=90, hjust=0, colour="black"))+
  #scale_fill_gradient(low = "red",high = "steelblue")
  theme_classic()

fd=data.frame(x = rep(c("x","y","z"),3), 
              y=c("a","b","c","b","c","a","c","a","b"),
              z=c(0,1,0,1,1,1,0,0,1))

# plot
p <- ggplot(fd, aes(x, y, height=.5, width=.5)) + geom_tile(aes(fill = z)) 
 + scale_fill_gradient(low = "white",high = "steelblue", limits=c(0,1)) 
 + theme_grey() 
 + labs(x = "", y= "") 
 + scale_x_discrete(expand = c(0, 0)) 
 + scale_y_discrete(expand = c(0, 0)) 
 + theme(legend.position = "none", axis.ticks = element_blank(), axis.text.x = element_text(size=12, angle=90, hjust=0, colour="black")))
```

```{r}
# outcome
out_start=2
out_end= 26
out_nvar=out_end-out_start+1

out_variable=rep(NA, out_nvar)
out_beta=rep(NA, out_nvar)
out_se = rep(NA, out_nvar)
out_pvalue=rep(NA, out_nvar)

# exposure
exp_start=27
exp_end=53
exp_nvar=exp_end-exp_start+1

exp_variable=rep(NA, exp_nvar)
exp_beta=rep(NA, exp_nvar)
exp_se = rep(NA, out_nvar)
exp_pvalue=rep(NA, exp_nvar)

number=1
```
```{r}
for (i in out_start:out_end){
  outcome = colnames(dat)[i]
  for (j in exp_start:exp_end){
    exposure = colnames(dat)[j]
    model <- lmer(get(outcome) ~ get(exposure) + v1 + (1|v2) + (1|v3),
      na.action = na.exclude,
      data=dat)

    Vcov <- vcov(model, useScale = FALSE)
    beta <- fixef(model)
    se <- sqrt(diag(Vcov))
    zval <- beta / se
    pval <- 2 * pnorm(abs(zval), lower.tail = FALSE)
    
    out_beta[number] = as.numeric(beta[2])
    out_se[number] = as.numeric(se[2])
    out_pvalue[number] = as.numeric(pval[2])
    out_variable[number] = outcome
    number = number + 1
    
    exp_beta[number] = as.numeric(beta[2])
    exp_se[number] = as.numeric(se[2])
    exp_pvalue[number] = as.numeric(pval[2])
    exp_variable[number] = exposure
    number = number + 1
  }
}
```
```{r}
outcome = data.frame(out_variable, out_beta, out_se, out_pvalue)
exposure = data.frame(exp_variable, exp_beta, exp_se, exp_pvalue)

library(tidyverse)
outcome = outcome %>% 
  rename(
    variable = out_variable,
    beta = out_beta,
    se = out_se,
    pvalue = out_pvalue,
    obs = out_nobs
    )
exposure = exposure %>% 
  rename(
    variable = exp_variable,
    beta = exp_beta,
    se = exp_se,
    pvalue = exp_pvalue,
    obs = exp_nobs
    )
all = rbind(outcome, exposure)
all = na.omit(all)

data = all %>% 
  mutate(type = substr(variable, 1, 2)) %>% 
  spread(type, variable) %>% 
  rename(d = dx,
         i = ix) %>% 
  mutate (beta = round(beta, 5),
          se = round(se, 5),
          pvalue = round(pvalue, 5)) %>% 
  select(d, i, beta, se, pvalue)
```

```{r}
wo.mul4 <- filter(dogg, Site != "MUL4")
wop <- lm(head.dmean ~ 
                slope.mean  +
                elev.mean + 
                UAA..ft2.,data = wo.mul4)
summary(wop)
```

AGGRESSION REGRESSION- run regressions predicting the daily mean of head temp, rather than one value for each site
```{r}
#subset data I actually need
atak <- select(dogg, Site, shed, Value, rnd.dates, d.mean, d.min, d.max, UAA..ft2., elev.mean, slope.mean, head.temp, head.dmean, airT, air.d.mean, air.d.min, air.d.max)%>%
  mutate(date = date(rnd.dates))
atak$rnd.dates <- ymd_hms(atak$rnd.dates)

#lm calculating one avg head temp value
h.avg.model <- lm(head.dmean ~ 
                slope.mean  +
                elev.mean + 
                UAA..ft2.,data = dogg)
summary(h.avg.model)
hair.avg.model <- lm(head.dmean ~ 
                slope.mean  +
                elev.mean + 
                UAA..ft2. +
                air.d.mean  ,data = dogg)
summary(hair.avg.model)

modeltester <- dogg%>%
  select(Site, shed, slope.mean, elev.mean, AREA, UAA..ft2., head.temp)%>%
  mutate(h.avg.model = 1.261e-01 * slope.mean + 
  -6.722e-04 * elev.mean + 
   5.125e-06 * UAA..ft2.+
   8.329e+00)%>%
  group_by(Site)%>%
  mutate(avg.head = mean(head.temp, na.rm = TRUE))
```

```{r}
#calculate lm for each day at each site
atak.day <- select(atak, -c(rnd.dates, Value, head.temp, airT))
atak.day <- unique(atak.day)
atak.day <- atak.day[complete.cases(atak.day),]

dayz <- select(atak.day, date)
dayz <- unique(dayz)

for(k in 1:length(dayz$date)){
  day <- dayz$date[k]
  df <- filter(atak.day, date == day)
  reg <- lm(head.dmean ~ air.d.mean + UAA..ft2. + elev.mean + slope.mean,
            data = df)
  r2 <- summary(reg)$r.squared
  #output
  temp <- mutate(df, r2 = r2)
  if(k == 1) alldat <- temp
  if(k > 1) alldat <- rbind(alldat, temp)
}

atakr.day <- alldat
ggplot(atakr.day, aes(x = date, y = r2))+
  geom_point()+
  theme_classic()
```
Just calculated for days


Calculate r2 for predicting every hour
```{r}
#calculate lm for each day at each site
atak.hour <- atak
atak.hour$hour <- floor_date(atak$rnd.dates, unit = "hour")
atak.hour <- atak.hour%>%
  group_by(hour, Site)%>%
  mutate(head.hmean = mean(head.temp), air.hmean = mean(airT))%>%
  select(Site, shed, hour, head.hmean, air.hmean, UAA..ft2., elev.mean, slope.mean)

atak.hour <- unique(atak.hour)
atak.hour <- atak.hour[complete.cases(atak.hour),]
atak.hour <- as.data.frame(atak.hour)

hourz <- select(atak.hour, hour)
hourz <- unique(hourz)

for(o in 1:length(hourz$hour)){
  our <- hourz$hour[o]
  df <- filter(atak.hour, hour == our)
  reg <- lm(head.hmean ~ air.hmean + UAA..ft2. + elev.mean + slope.mean,
            data = df)
  r2 <- summary(reg)$r.squared
  #output
  temp <- mutate(df, r2 = r2)
  if(o == 1) alldat <- temp
  if(o > 1) alldat <- rbind(alldat, temp)
}

atakr.hour <- alldat
ggplot(atakr.hour, aes(x = hour, y = r2))+
  geom_point()+
  theme_classic()

gour <- atakr.hour%>%
  select(Site, shed, hour, head.hmean, air.hmean, r2)
```


Calculate r2 at different time scales using the time every ten minutes
```{r}
#calculate lm for each 10 min interval at each site
atak.min <- unique(atak)
atak.min <- atak.min[complete.cases(atak.min),]

minz <- select(atak.min, rnd.dates)
minz <- unique(minz)

for(o in 1:length(minz$rnd.dates)){
  mint <- minz$rnd.dates[o]
  df <- filter(atak.min, rnd.dates == mint)
  reg <- lm(head.temp ~ airT + UAA..ft2. + elev.mean + slope.mean,
            data = df)
  r2 <- summary(reg)$r.squared
  #output
  temp <- mutate(df, r2 = r2)
  if(o == 1) alldat <- temp
  if(o > 1) alldat <- rbind(alldat, temp)
}

atakr.min <- alldat
mast <- atakr.min%>%
  rename(r2.minpmin = r2) #minpmin- min pred by actual measurements, 10 min inc values
mast$hour <- floor_date(mast$rnd.dates, unit = "hour")


mast <- left_join(mast, gour, by = c("Site", "shed", "hour"))%>% #hour pred by hmean
  rename(r2.hourphour = r2)

gai <- select(atakr.day, Site, shed, date, r2)
mast <- left_join(mast, gai,  by = c("Site", "shed", "date"))%>% #day pred by dmean
  rename(r2.daypday = r2)

#Calculate
#day pred by min
#hour pred by min
for(o in 1:length(minz$rnd.dates)){
  mint <- mast$rnd.dates[o]
  df <- filter(mast, rnd.dates == mint)
  reg <- lm(head.dmean ~ airT + UAA..ft2. + elev.mean + slope.mean,
            data = df)
  reg2 <- lm(head.hmean ~ airT + UAA..ft2. + elev.mean + slope.mean,
            data = df)
  r2 <- summary(reg)$r.squared
  r2.2 <- summary(reg2)$r.squared
  #output
  temp <- mutate(df, daypmin = r2, hourpmin = r2.2)
  if(o == 1) alldat <- temp
  if(o > 1) alldat <- rbind(alldat, temp)
}

hup <- select(alldat, Site, shed, rnd.dates, daypmin, hourpmin)
mast <- left_join(mast, hup, by = c("Site", "shed", "rnd.dates"))%>%
  rename(r2.daypmin = daypmin, r2.hourpmin = hourpmin)

masty <- unique(mast)
hasty <- select(masty, rnd.dates, r2.daypday, r2.hourphour, r2.minpmin)%>%
  gather(key = "r2.type", value = "value", -rnd.dates)

hasty$r2.type <- factor(hasty$r2.type)
hasty$r2.type <- factor(hasty$r2.type, levels = c("r2.minpmin","r2.daypday", "r2.hourphour"))
hasty <- unique(hasty)

p <-ggplot(hasty, aes(x = rnd.dates,
                      y = value))+
  geom_boxplot(aes(color = r2.type))+
  theme_classic()
p  
#xlim("2019-07-02 12:00:00 UTC", "2019-07-06 12:00:00 UTC")
```
