---
title: "Further Analysis 9_3"
output: html_document
---

9/3
Goal is to conduct further analysis discussed in July with JP and Christa, also want to work with the data and get familiar with the numbers. 

9/5
Thought that I succeeded before, but it would appear I did not- something wrong with the calculated values- won't plot, I think there is something wrong with how I tried to calculate the data metrics
```{r global_options, include=FALSE}
#global settings
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

```{r}
#Packages
library(tidyverse)
library(lubridate)
```

Using Tibbles
```{r}
#printing more than tibble does by default
temps %>% print(n = 10, width = Inf)
#changes tibble printing defaults
#print all rows
#options(tibble.print_min = Inf)
#print all columns
options(tibble.width = Inf)
```

```{r}
#Reading in old output csv, fully formatted and edited
temps <- read_csv("Formatted.temps.tall_7_17.csv")
                  
                  
                 
#format time
temps$rnd.dates <- ymd_hms(temps$rnd.dates)

temps <- temps %>% mutate(day = day(rnd.dates))
temps <- temps %>% mutate(month = month(rnd.dates))
#making data frame to number the unique days- 1-26
day <- unique(temps$day)
do <- seq(1,26,1)
undo <- data.frame(day, do)
#number unique days
temps <- inner_join(temps, undo, by = "day")
#making data frame to number unique hours
temps <- temps %>% mutate(hour = floor_date(rnd.dates, "hour"))


#calculation daily mean, min, max, sd
temps <- temps %>% group_by(do) %>% mutate(d.mean = mean(Value, na.rm = TRUE))
                                           
                                    
                                           d.min = min(Value, na.rm = TRUE),
                                           d.max = max(Value, na.rm = TRUE),
                                           d.sd = sd(Value, na.rm = TRUE))
ungroup(temps)
#calculating hourly mean, min, max, sd
temps <- temps %>% group_by(hour) %>% mutate(h.mean = mean(Value),
                                             h.min = min(Value),
                                             h.max = max(Value),
                                             h.sd = sd(Value))
ungroup(temps)

temps <- temps %>% mutate_each(list(as.factor), sensor)

#making sure my data stuff worked- I don't think it did
test <- temps %>% filter(sensor == c("130", "78"))
write.csv(test, file = "test9_5.csv")
```

Successfully calculated metrics, now going to plot em
```{r}
daily <- ggplot(data = test)+
  geom_line(aes(x = rnd.dates, 
                y = d.mean,
                color = sensor))+
  theme_classic()
daily

daily2 <- ggplot()
```

Previous effort failed, trying to subset a different way- do each sensor individually, then combine them after calculating the mean and other metrics
```{r}
#Reading in old output csv, fully formatted and edited
raw <- read.csv("Formatted.temps.tall_7_17.csv")
raw$rnd.dates <- ymd_hms(raw$rnd.dates)
raw <- raw %>% mutate_each(list(as.factor), sensor)

one.three.zero <- raw %>% filter(sensor == "130")
seventy.eight <- raw %>% filter(sensor == "78")

seventy.eight <- seventy.eight %>% mutate(day = day(rnd.dates))
seventy.eight <- as_tibble(seventy.eight)
seventy.eight <- seventy.eight %>% 
  group_by(day) %>% 
  mutate(d.mean = mean(Value, na.rm = TRUE))

one.three.zero <- one.three.zero %>% mutate(day = day(rnd.dates))
one.three.zero <- as_tibble(one.three.zero)
one.three.zero <- one.three.zero %>% 
  group_by(day) %>% 
  mutate(d.mean = mean(Value, na.rm = TRUE))

test <- bind_rows(seventy.eight, one.three.zero)
```

Going to try it again- using the old method but with some new consideration on how data should be formatted
```{r}
temps <- read_csv("Formatted.temps.tall_7_17.csv")
temps <- temps %>% mutate_each(list(as.factor), sensor)
#re ordering the variables to make them tidy
yeti <- temps %>% select(site, sensor, shed, type, Value, rnd.dates)

groo <- yeti %>% filter(shed == "ULB", site != "ULBAir")

groop <- ggplot(groo)+
  geom_line(aes(x = rnd.dates,
                y = Value,
                color = site))+
  theme_classic()

goons <- yeti %>% 
  group_by(site, day = day(rnd.dates))

sum.goons <- goons %>% 
  summarise(d.mean = mean(Value, na.rm = TRUE))

sum.goons.1 <- sum.goons %>% select(site, day)
sum.goons.2 <- sum.goons %>% select(site, d.mean)

ungroup(goons)
ungroup(sum.goons.1)
#this works!!
goons2 <- semi_join(goons, sum.goons.1, by = "site")
#this works even better!
goons3 <- left_join(goons, sum.goons, by = c("site", "day"))

stick <- inner_join(yeti, sum.goons, by = "site")
goose <- left_join(yeti, sum.goons, by = "site")

sticky <- ggplot(data = stick)+
  geom_line(aes(x = day,
                y = d.mean,
                color = site))

```

9/10
I believe I am having great success- going to finally make the finalized table, and then try to subset and graph some stuff
```{r}
temps <- read_csv("Formatted.temps.tall_7_17.csv")
temps <- temps %>% mutate_each(list(as.factor), sensor)
#re ordering the variables to make them tidy
yeti <- temps %>% select(site, sensor, shed, type, Value, rnd.dates)

#adding a day column

yeti <- yeti
yeti$numb <- str_sub(yeti$site, 4, 5)
yeti$A.B <- str_sub(yeti$site, 6, 6)
yeti <- select(yeti, site, sensor, shed, type, numb, A.B, Value, rnd.dates)
#only use numb and A.B variables if not working with air temps- only useful for plotting and subsetting stream sites
yeti <- yeti %>% mutate_each(list(as.character), numb)

#omitting missing values
yeti <- na.omit(yeti)

goons <- yeti %>% 
  group_by(site, day = day(rnd.dates))
#making summary of each day
sum.goons <- goons %>% 
  summarise(d.mean = mean(Value), 
            d.min = min(Value),
            d.max = max(Value),
            d.sd = sd(Value))
#unsure if these are needed
ungroup(goons)
ungroup(sum.goons.1)
#adding summary table to temps
goons3 <- left_join(goons, sum.goons, by = c("site", "day"))
#successfully made a table with daily metrics
#save table
#write.csv(goons3, file = "Tempswithdmetrics10_3.csv")

```

Making plots using daily metrics table
```{r}
day <- goons3

sheds <- c("ULB", "GG", "RMO", "MUL")
ULB.day <- filter(day, shed == "ULB", type != "air")
GG.day <- filter(day, shed == "GG", type != "air")
RMO.day <- filter(day, shed == "RMO", type != "air")
MUL.day <- filter(day, shed == "MUL", type != "air")

for (i in 1:length(sheds)) {
  f <- filter(day, shed == sheds[i], type != "air")  
  plot <- ggplot(data = f)+
    geom_point(aes(x = d.max - d.min,
                  y = d.mean,
                  color = site,
                  shape = type
                  ))
    #xlim(8,25)+
    #ylim(8,25)
  print(plot)
}
```

9/12
I am going to try to produce some good plots, based on the code that I was working on the 10th
```{r}
ulb.r <- c("ULB2HA", "ULB2CB","ULB3HA", "ULB3CB", "ULB4HA", "ULB4CA")
rmo.r <- c("RMO1HA", "RMO1CB", "RMO2HA", "RMO2CB", "RMO3HB", "RMO3CB")
mul.r <- c("MUL2HA", "MUL2CB", "MUL4HB", "MUL4CA", "MUL7HB", "MUL7CA") 
gg.r <- c("W600B", "W400A", "GC300B","GC100B", "LS180B", "LS0B")
air.r <- c("MULAir", "GGAir", "ULBAir", "RMOAir")
sites <- c(ulb.r, rmo.r, mul.r, gg.r, air.r)

day <- filter(goons3, site %in% sites)

ULB.a <- filter(day, shed == "ULB")
ULB.w <- filter(day, shed == "ULB", type != "air")
GG.a <- filter(day, shed == "GG")
GG.w <- filter(day, shed == "GG", type != "air")
RMO.a <- filter(day, shed == "RMO")
RMO.w <- filter(day, shed == "RMO", type != "air")
MUL.a <- filter(day, shed == "MUL")
MUL.w <- filter(day, shed == "MUL", type != "air")
fils <- c(ULB.day, GG.day, RMO.day, MUL.day)

plot <- ggplot(data = ULB.a)+
    geom_line(aes(x = rnd.dates,
                  y = d.max,
                  color = site,
                  shape = type
                  ))+
  geom_line(aes(x = rnd.dates,
                  y = d.min,
                  color = site,
                  shape = type
                  ))
  print(plot)
  
#plot 
```

