---
title: "R Notebook"
output: html_notebook
---
7/10/19
Yesterday I finished collecting all of my temperature sensors, and today begins the data analysis. 

Goals for today:
  Figure out how to use Github
  Format temperature data

Work flow
I've got an individual csv file for each sensor, so I need to read all of these in and combine the data. I need to rename each number to the sensor location. I need to round all the times to the nearest 10 minute interval so they line up.

```{r global_options, include=FALSE}
#global settings
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

```{r}
#Packages
library(tidyr)
library(dplyr)
library(ggplot2)
library(ggridges)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}

```

