---
title: "R Notebook"
output: html_notebook
---
7/10/19
Yesterday I finished collecting all of my temperature sensors, and today begins the data analysis. 

Goals for today:
  Figure out how to use Github
  Format temperature data

Work flow
I've got an individual csv file for each sensor, so I need to read all of these in and combine the data. I need to rename each number to the sensor location. I need to round all the times to the nearest 10 minute interval so they line up.

```{r global_options, include=FALSE}
#global settings
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

```{r}
#Packages
library(tidyr)
library(dplyr)
library(ggplot2)
library(ggridges)
library(lubridate)
#add ggsave to export stuff
#library(ggsave)
```

```{r}
#read in all the csv files
files <- list.files(path = "Temp data 7_9_19 raw/")
sites <- read.csv("site_temps_7_11.csv", header = T, sep = ",")
    sites$f.col.time <- mdy_hm(sites$collection.time)
    sites$f.dep.time <- mdy_hm(sites$deploy.time)

for (i in 1:length(files)) {
    data <- read.csv(paste0("Temp data 7_9_19 raw/",
                            files[i]), 
                     skip = 19, 
                     header = T, sep = ",")
    #formatting time
    data$fdates <- mdy_hms(data$Date.Time)
    #making a column with sensor number
    data$sensor <- files[i]
    data$sensor <- gsub("data","\\1", data$sensor)
    data$sensor <- gsub(".csv","\\1", data$sensor)
    #making column with site loc
    #round temperatures to nearest tenth
    data$rnd.dates <- round_date(data$fdates, "10 minutes")
  
  if(i == 1)alldat <- data                 
  if(i > 1)alldat <- rbind(alldat, data)
}

```

Format the data to work with.
```{r}
#formatting data to remove undeployed sensors

#finding ones that weren't deployed
data.sensors <- unique(alldat$sensor)
sites.sensors <- unique(sites$sensor)
diff <- setdiff(data.sensors, sites.sensors)
#removing sensors that weren't deployed
alldat <- filter(alldat, sensor %in% sites$sensor)
#add site location column
alldat$sensor <- as.numeric(alldat$sensor)
#removed sensor 54- something wrong
#alldat2 <- filter(alldat, sensor != 54)
#adding sites data sheet- matching sensors with sites
alldat2 <- inner_join(alldat, sites, by = "sensor")
#identify list of sites
locs <- unique(alldat2$site)

#formatting time to beginning and end of deployment period
start <- mdy_hm("6-13-19 13:10")
end <- mdy_hm("7-8-19 11:20")
alldat3 <- filter(alldat2, rnd.dates >= start)
alldat3 <- filter(alldat3, rnd.dates <= end)

master <- select(alldat3, Value, sensor, rnd.dates, site)
master$rnd.dates <- as.POSIXct(master$rnd.dates, format = "%Y-%M-%d %H:%M:%S")

```

Before I can plot, I have to subset the data in ways that I want it all plotted
```{r}
#plotting time!
#heads
sites.heads <- c("ULB2HA", "ULB3HA", "ULB4HA", "W600A", "GC300A", "LS180A", "MUL2HA", "MUL4HA", "MUL7HA", "RMO1HA", "RMO2HA", "RMO3HA")
head <- filter(master, site %in% sites.heads)
heads.plot <- ggplot(data = heads)+
  geom_line(aes(x = rnd.dates, 
                y = Value,
                color = site))+
  #ylim(10, 15)+
  theme_classic()
heads.plot

ulb.heads <- c("ULB2HA","ULB2HB", "ULB3HB", "ULB3HA", "ULB4HA")
ulb.head <- filter(master, site %in% ulb.heads)
ulb.heads.plot <- ggplot(data = ulb.head)+
  geom_line(aes(x = rnd.dates, 
                y = Value,
                color = site))+
  theme_classic()
ulb.heads.plot

mul.heads <- c("MUL2HA","MUL2HB", "MUL4HA", "MUL4HB", "MUL7HA", "MUL7HB", "MULAir")
mul.head <- filter(master, site %in% mul.heads)
mul.heads.plot <- ggplot(data = mul.head)+
  geom_line(aes(x = rnd.dates,
                y = Value,
                color = site))+
  ylim(0, 20)+
  theme_classic()
mul.heads.plot

rmo.heads <- c("RMO1CA", "RMO1HB", "RMO2CA", "RMO2HB", "RMO3CA", "RMO3HB")
rmo.head <- filter(master, site %in% rmo.heads)
rmo.heads.plot <- ggplot(data = rmo.head)+
  geom_line(aes(x = rnd.dates,
                y = Value,
                color = site))+
  theme_classic()
rmo.heads.plot

gg.heads <- c("W600A", "W600B", "GC300A", "GC300B", "LS180A", "LS180B")
gg.head <- filter(master, site %in% gg.heads)
gg.heads.plot <- ggplot(data = gg.head)+
  geom_line(aes(x = rnd.dates,
                y = Value,
                color = site))+
  ylim(10, 20)+
  theme_classic()
gg.heads.plot

airs <- c("ULBAir", "GGAir", "MULAir", "RMOAir")
air <- filter(master, site %in% airs)
air.plot <- ggplot(data = air)+
  geom_line(aes(x = rnd.dates,
                y = Value,
                color = site))+
  ylim(0, 28)+
  theme_classic()
air.plot
#air temp analysis
master.spread <- select(master, Value, rnd.dates, site)
master.spread <- master.spread %>% spread(site, value = Value)
air.diff <- 
```

```{r}
#ULB
#trying to figure out if my data is real
ulb.2 <- c("ULB2HA", "ULB2HB", "ULB2CA", "ULB2CB")
ulb.3 <- c("ULB3HA", "ULB3HB", "ULB3CA", "ULB3CB")
ulb.4 <- c("ULB4HA", "ULB4CB", "ULB4CA") #removed HB
#rmo
rmo.1 <- c("RMO1HA", "RMO1HB", "RMO1CA", "RMO1CB")
rmo.2 <- c("RMO2HA", "RMO2HB", "RMO2CA", "RMO2CB")
rmo.3 <- c("RMO3HA", "RMO3HB", "RMO3CA", "RMO3CB")
#mul
mul.2 <- c("MUL2HA", "MUL2HB", "MUL2CA", "MUL2CB")
mul.4 <- c("MUL4HB", "MUL4CA") #removed HA, CB missing
mul.7 <- c("MUL7HB", "MUL7CA", "MUL7CB") #removed HA, weird spike and like downstream- bc of how it goes subsurface bewteen sites I think
#gg
gg.1 <- c("W600A", "W600B", "W400A", "W400B") #removed W600A, super shallow/in sun, weird spike
gg.2 <- c("GC300B", "GC100A", "GC100B") #GC300A is missing, spike in 300B but is visible downstream
gg.3 <- c("LS180B", "LS0A", "LS0B")

cal <- filter(master, site %in% gg.3)
c.plot <- ggplot(data = cal)+
  geom_line(aes(x = rnd.dates,
                y = Value,
                color = site))+
  #ylim(12, 19)+
  theme_classic()
c.plot
```

