---
title: "R Notebook"
output: html_notebook
---
7/10/19
Yesterday I finished collecting all of my temperature sensors, and today begins the data analysis. 

Goals for today:
  Figure out how to use Github
  Format temperature data

Work flow
I've got an individual csv file for each sensor, so I need to read all of these in and combine the data. I need to rename each number to the sensor location. I need to round all the times to the nearest 10 minute interval so they line up.

```{r global_options, include=FALSE}
#global settings
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

```{r}
#Packages
library(tidyr)
library(dplyr)
library(ggplot2)
library(ggridges)
library(lubridate)
```

```{r}
#read in all the csv files
files <- list.files(path = "Temp data 7_9_19 raw/")
sites <- read.csv("site_temps_7_11.csv", header = T, sep = ",")
    sites$f.col.time <- mdy_hm(sites$collection.time)
    sites$f.dep.time <- mdy_hm(sites$deploy.time)

#t <- minutes(10)
#list of site locs in order by sensor numbers?

for (i in 1:length(files)) {
    data <- read.csv(paste0("Temp data 7_9_19 raw/",
                            files[i]), 
                     skip = 19, 
                     header = T, sep = ",")
    #formatting time
    data$fdates <- mdy_hms(data$Date.Time)
    #making a column with sensor number
    data$sensor <- files[i]
    data$sensor <- gsub("data","\\1", data$sensor)
    data$sensor <- gsub(".csv","\\1", data$sensor)
    #making column with site loc
    #cbind(data, site = sites[i])
    #round temperatures to nearest tenth
    data$rnd.dates <- round_date(data$fdates, "10 minutes")
  
  if(i == 1)alldat <- data                 
  if(i > 1)alldat <- rbind(alldat, data)
  #row.names(datasetname) <- 1:nrow(datasetname)
  #alldat$fdates <- mdy_hms(alldat$Date.Time)
  #alldat$rdates <- round_date()
  
}

```

```{r}
#formatting data to remove undeployed sensors
data.sensors <- unique(alldat$sensor)
sites.sensors <- unique(sites$sensor)
diff <- setdiff(data.sensors, sites.sensors)
alldat <- filter(alldat, sensor %in% sites$sensor)
#not sure if it worked

#add site location column
alldat <- mutate(alldat, loc = 2)
alldat <- mutate(alldat, loc = sites$site[sites$sensor == alldat$sensor])

alldat$sensor <- as.numeric(alldat$sensor)
alldat2 <- inner_join(alldat, sites, by = "sensor")

```

Problems:
  when i call up the row by number, it gives me multiple instances of it
  
```{r}
#plotting time!
all.temps <- ggplot()+
  geom_boxplot(alldat, 
                      mapping = aes(y = Value, x = sensor))+  theme_classic()+
  xlab("Temp (C)")
all.temps
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}

```

