---
title: "R Notebook"
output: html_notebook
---
7/10/19
Yesterday I finished collecting all of my temperature sensors, and today begins the data analysis. 

Goals for today:
  Figure out how to use Github
  Format temperature data

Work flow
I've got an individual csv file for each sensor, so I need to read all of these in and combine the data. I need to rename each number to the sensor location. I need to round all the times to the nearest 10 minute interval so they line up.

```{r global_options, include=FALSE}
#global settings
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

```{r}
#Packages
library(tidyr)
library(dplyr)
library(ggplot2)
library(ggridges)
library(lubridate)
library(SAVER)
#add ggsave to export stuff
#library(ggsave)
```

```{r}
#read in all the csv files
#removed 15- ULB4HB- super messed up, sensor was broken
files <- list.files(path = "Temp data 7_9_19 raw/")
sites <- read.csv("site_temps_7_11.csv", header = T, sep = ",")
    sites$f.col.time <- mdy_hm(sites$collection.time)
    sites$f.dep.time <- mdy_hm(sites$deploy.time)

for (i in 1:length(files)) {
    data <- read.csv(paste0("Temp data 7_9_19 raw/",
                            files[i]), 
                     skip = 19, 
                     header = T, sep = ",")
    #formatting time
    data$fdates <- mdy_hms(data$Date.Time)
    #making a column with sensor number
    data$sensor <- files[i]
    data$sensor <- gsub("data","\\1", data$sensor)
    data$sensor <- gsub(".csv","\\1", data$sensor)
    #making column with site loc
    #round temperatures to nearest tenth
    data$rnd.dates <- round_date(data$fdates, "10 minutes")
  
  if(i == 1)alldat <- data                 
  if(i > 1)alldat <- rbind(alldat, data)
}

```

Format the data to work with.
```{r}
#formatting data to remove undeployed sensors

#finding ones that weren't deployed
data.sensors <- unique(alldat$sensor)
sites.sensors <- unique(sites$sensor)
diff <- setdiff(data.sensors, sites.sensors)
#removing sensors that weren't deployed
alldat <- filter(alldat, sensor %in% sites$sensor)
#add site location column
alldat$sensor <- as.numeric(alldat$sensor)
#removed sensor 54- something wrong
#alldat2 <- filter(alldat, sensor != 54)
#adding sites data sheet- matching sensors with sites
alldat2 <- inner_join(alldat, sites, by = "sensor")
#identify list of sites
locs <- unique(alldat2$site)

#formatting time to beginning and end of deployment period
start <- mdy_hm("6-13-19 13:10")
end <- mdy_hm("7-8-19 11:20")
alldat3 <- filter(alldat2, rnd.dates >= start)
alldat3 <- filter(alldat3, rnd.dates <= end)

master <- select(alldat3, Value, sensor, rnd.dates, site, type, shed)
#replacing wacky temps with NA
which(master$Value == -41, arr.ind = T)
master$Value[74005] <- NA
master$Value[which(master$Value > 35, arr.ind = T)] <- NA
#setting everything below 0 = NA, it didn't get below 0
master$Value[which(master$Value < 0, arr.ind = T)] <- NA
master$rnd.dates <- as.POSIXct(master$rnd.dates, format = "%Y-%M-%d %H:%M:%S")

```

Before I can plot, I have to subset the data in ways that I want it all plotted
```{r}
#plotting time!
#heads
sites.heads <- c("ULB2HA", "ULB3HA", "ULB4HA", "W600A", "GC300A", "LS180A", "MUL2HA", "MUL7HA", "RMO1HA", "RMO2HA", "RMO3HA")
head <- filter(master, site %in% sites.heads)
heads.plot <- ggplot(data = head)+
  geom_line(aes(x = rnd.dates, 
                y = Value,
                color = site))+
  #ylim(10, 15)+
  theme_classic()
heads.plot

ulb.heads <- c("ULB2HA","ULB2HB", "ULB3HB", "ULB3HA", "ULB4HA")
ulb.head <- filter(master, site %in% ulb.heads)
ulb.heads.plot <- ggplot(data = ulb.head)+
  geom_line(aes(x = rnd.dates, 
                y = Value,
                color = site))+
  theme_classic()
ulb.heads.plot

mul.heads <- c("MUL2HA","MUL2HB", "MUL4HB", "MUL7HB", "MULAir")
mul.head <- filter(master, site %in% mul.heads)
mul.heads.plot <- ggplot(data = mul.head)+
  geom_line(aes(x = rnd.dates,
                y = Value,
                color = site))+
  ylim(0, 20)+
  theme_classic()
mul.heads.plot

rmo.heads <- c("RMO1CA", "RMO1HB", "RMO2CA", "RMO2HB", "RMO3CA", "RMO3HB")
rmo.head <- filter(master, site %in% rmo.heads)
rmo.heads.plot <- ggplot(data = rmo.head)+
  geom_line(aes(x = rnd.dates,
                y = Value,
                color = site))+
  theme_classic()
rmo.heads.plot

gg.heads <- c("W600A", "W600B", "GC300A", "GC300B", "LS180A", "LS180B")
gg.head <- filter(master, site %in% gg.heads)
gg.heads.plot <- ggplot(data = gg.head)+
  geom_line(aes(x = rnd.dates,
                y = Value,
                color = site))+
  ylim(10, 20)+
  theme_classic()
gg.heads.plot

airs <- c("ULBAir", "GGAir", "MULAir", "RMOAir")
air <- filter(master, site %in% airs)
air.plot <- ggplot(data = air)+
  geom_line(aes(x = rnd.dates,
                y = Value,
                color = site))+
  ylim(0, 28)+
  theme_classic()
air.plot

```

```{r}
#ULB
#trying to figure out if my data is real
ulb.2 <- c("ULB2HA", "ULB2HB", "ULB2CA", "ULB2CB")
ulb.3 <- c("ULB3HA", "ULB3HB", "ULB3CA", "ULB3CB")
ulb.4 <- c("ULB4HA", "ULB4CB", "ULB4CA") #removed HB
#rmo
rmo.1 <- c("RMO1HA", "RMO1HB", "RMO1CA", "RMO1CB")
rmo.2 <- c("RMO2HA", "RMO2HB", "RMO2CA", "RMO2CB")
rmo.3 <- c("RMO3HA", "RMO3HB", "RMO3CA", "RMO3CB")
#mul
mul.2 <- c("MUL2HA", "MUL2HB", "MUL2CA", "MUL2CB")
mul.4 <- c("MUL4HB", "MUL4CA") #removed HA, CB missing
mul.7 <- c("MUL7HB", "MUL7CA", "MUL7CB") #removed HA, weird spike and like downstream- bc of how it goes subsurface bewteen sites I think
#gg
gg.1 <- c("W600A", "W600B", "W400A", "W400B") #removed W600A, super shallow/in sun, weird spike
gg.2 <- c("GC300B", "GC100A", "GC100B") #GC300A is missing, spike in 300B but is visible downstream
gg.3 <- c("LS180B", "LS0A", "LS0B")

cal <- filter(master, site %in% gg.3)
c.plot <- ggplot(data = cal)+
  geom_line(aes(x = rnd.dates,
                y = Value,
                color = site))+
  #ylim(12, 19)+
  theme_classic()
c.plot
```

Ridge plots- show distribution
JP was thinking I should make them with both the channel head and downstream sites together and color coded by elevation- we shall see
```{r}
cal <- filter(master)
rigged <- ggplot()+
  geom_density_ridges2(cal, 
                      mapping = aes(x = Value,
                                    y=site,
                                    scale=1,
                                    fill = site))+
  #scale_x_continuous(limits=c(8,12))+
  theme_classic()+
  scale_fill_brewer(palette = "Dark2")+
  theme(axis.title.y=element_blank(),
        axis.ticks.y=element_blank(),
        strip.text.y = element_text(angle = 180, hjust = 1),
        line = element_blank())+
  scale_x_continuous( expand = c(0.01, 0)) +
  scale_y_discrete(expand = c(0.001, 0))+
  xlab("Temp (C)")
rigged
```

Spreading the data in order to do some math between heads and downstream sites
```{r}
master.spread <- select(master, Value, rnd.dates, site)
master.spread <- master.spread %>% spread(site, value = Value)
#all diffs
#channel t - head t
attach(master.spread)
master.diffs <- data.frame("time" = rnd.dates,
                           "ULB2"= ULB2CA - ULB2HA,
                           "ULB3"= ULB3CA - ULB3HA,
                           "ULB4"= ULB4CA - ULB4HA,
                           "RMO1" = RMO1CA - RMO1HA,
                           "RMO2" = RMO2CA - RMO2HA,
                           "RMO3" = RMO3CA - RMO3HB,
                           "MUL2" = MUL2CA - MUL2HA,
                           "MUL4" = MUL4CA - MUL4HB,
                           "MUL7" = MUL7CA - MUL7HB,
                           "W" = W400A - W600A,
                           "GC" = GC100A - GC300B,
                           "LS" = LS0B - LS180B)
detach(master.spread)

#gathering data into tall boy
tall.diffs <- master.diffs %>% gather(site, temp, -time)

all.diffs.plot <- ggplot()+
  geom_density_ridges2(tall.diffs, 
                      mapping = aes(x = temp,
                                    y=site,
                                    scale=1,
                                    ))+
  #scale_x_continuous(limits=c(8,12))+
  theme_classic()+
  scale_fill_brewer(palette = "Dark2")+
  theme(axis.title.y=element_blank(),
        axis.ticks.y=element_blank(),
        strip.text.y = element_text(angle = 180, hjust = 1),
        line = element_blank())+
  scale_x_continuous( expand = c(0.01, 0)) +
  scale_y_discrete(expand = c(0.001, 0))+
  xlab("Temp (C)")
all.diffs.plot
```
  
Plots of diff vs air
```{r}
attach(master.spread)
ulb.diffs <- data.frame("ULB2"= ULB2CA - ULB2HA,
                           "ULB3"= ULB3CA - ULB3HA,
                           "ULB4"= ULB4CA - ULB4HA,
                            "ULBAir" = ULBAir)
rmo.diffs <- data.frame(
                           "RMO1" = RMO1CA - RMO1HA,
                           "RMO2" = RMO2CA - RMO2HA,
                           "RMO3" = RMO3CA - RMO3HB,
                           "RMOAir" = RMOAir
                           )
mul.diffs <- data.frame(
                           "MUL2" = MUL2CA - MUL2HA,
                           "MUL4" = MUL4CA - MUL4HB,
                           "MUL7" = MUL7CA - MUL7HB,
                           "MULAir" = MULAir)
gg.diffs <- data.frame(
                           "GGAir" = GGAir,
                           "W" = W400A - W600A,
                           "GC" = GC100A - GC300B,
                           "LS" = LS0B - LS180B)
elev.diff <- data.frame()
detach(master.spread)

#make em tall- wtih ULBAir as the spreader
ulb.tall.diffs <- ulb.diffs %>% gather(site, temp, -ULBAir)
gg.tall.diffs <- gg.diffs %>% gather(site, temp, -GGAir)
rmo.tall.diffs <- rmo.diffs %>% gather(site, temp, -RMOAir)
mul.tall.diffs <- mul.diffs %>% gather(site, temp, -MULAir)

gg.diff.plot <- ggplot(data = gg.tall.diffs, 
                       aes(x = GGAir,
                           y = temp,
                           color = site))+
  scale_color_brewer(palette = "Dark2",
                     name = "Stream")+
  stat_density2d(size = 2)+
  ylab("Downstream Temp - Head Temp (C)")+
  xlab("Air Temperature (C)")+
  theme_classic()+
  theme(text= element_text(size=17))
gg.diff.plot
#ulb
ulb.diff.plot <- ggplot(data = ulb.tall.diffs, 
                       aes(x = ULBAir,
                           y = temp,
                           color = site))+
  scale_color_brewer(palette = "Dark2",
                     name = "Stream")+
  stat_density2d(size = 2)+
  ylab("Downstream Temp - Head Temp (C)")+
  xlab("Air Temperature (C)")+
  theme_classic()+
  theme(text= element_text(size=17))
ulb.diff.plot
#rmo
rmo.diff.plot <- ggplot(data = rmo.tall.diffs, 
                       aes(x = RMOAir,
                           y = temp,
                           color = site))+
  scale_color_brewer(palette = "Dark2",
                     name = "Stream")+
  stat_density2d(size = 2)+
  ylab("Downstream Temp - Head Temp (C)")+
  xlab("Air Temperature (C)")+
  theme_classic()+
  theme(text= element_text(size=17))
rmo.diff.plot
#mul
mul.diff.plot <- ggplot(data = mul.tall.diffs, 
                       aes(x = MULAir,
                           y = temp,
                           color = site))+
  scale_color_brewer(palette = "Dark2",
                     name = "Stream")+
  stat_density2d(size = 2)+
  ylab("Downstream Temp - Head Temp (C)")+
  xlab("Air Temperature (C)")+
  theme_classic()+
  theme(text= element_text(size=17))
mul.diff.plot

ggsave("ulb.dif.png", plot = ulb.diff.plot, width = 7, height = 5, units = c("in"))
ggsave("mul.diff.png", plot = mul.diff.plot, width = 7, height = 5, units = c("in"))
ggsave("rmo.diff.png", plot = rmo.diff.plot, width = 7, height = 5, units = c("in"))
ggsave("gg.diff.png", plot = gg.diff.plot, width = 7, height = 5, units = c("in"))

```
  
7-15-19
Final Plots that are going on the SURP poster
  Goals: Convey general temperature trends:
    -that the channel heads have almost constant temperatures
    -that stream water is cooler in high elevations
    -explore the relationship between mean annual air temperature and groundwater temperature
    - explore how water warms at different elevations and distances

Plots I will make:
  -ridge plots with head and c
  -general timeseries
  -Head vs airT
  -mean airT vs mean waterT
  -mean airT vs mean diff or diff vs airT
  
Ridge plots with head and C
```{r}
#ULB
ulb.r <- c("ULB2HA", "ULB2CB","ULB3HA", "ULB3CB", "ULB4HA", "ULB4CA")
#rmo
rmo.r <- c("RMO1HA", "RMO1CB", "RMO2HA", "RMO2CB", "RMO3HB", "RMO3CB")
#mul
mul.r <- c("MUL2HA", "MUL2CB", "MUL4HB", "MUL4CA", "MUL7HB", "MUL7CA") 
#gg
gg.r <- c("W600B", "W400A", "GC300B","GC100B", "LS180B", "LS0B")
#labels
labelz <- c("Head", "Downstream", "Head", "Downstream", "Head", "Downstream") 
#subset master dataset
ulb.r <- filter(master, site %in% ulb.r)
rmo.r <- filter(master, site %in% rmo.r)
mul.r <- filter(master, site %in% mul.r)
gg.r <- filter(master, site %in% gg.r)
#change variable names to remove A/B
ulb.r$site <- gsub('.{1}$', '', ulb.r$site)
rmo.r$site <- gsub('.{1}$', '', rmo.r$site)
mul.r$site <- gsub('.{1}$', '', mul.r$site)
gg.r$site <- gsub('.{1}$', '', gg.r$site)
#make ridge plots
#ulb
ulb.ridge <- ggplot()+
  geom_density_ridges2(ulb.r,fill = c('midnightblue'),
                      mapping = aes(x = Value,
                                    y=site,
                                    scale=1))+
  theme_classic()+
  theme(axis.title.y=element_blank(),
        axis.title.x=element_text(size = 17),
        axis.ticks.y=element_blank(),
        strip.text.y = element_text(angle = 180, hjust = 1),
        line = element_blank(),
        axis.text.x = element_text(size = 17),
        axis.text.y = element_text(size = 17))+
  scale_x_continuous( expand = c(0.01, 0)) +
  scale_y_discrete(expand = c(0.001, 0))+
  xlab("Temp (C)")
ulb.ridge
#rmo
rmo.ridge <- ggplot()+
  geom_density_ridges2(rmo.r,fill = c('sienna1'),
                      mapping = aes(x = Value,
                                    y=site,
                                    scale=1))+
  theme_classic()+
  theme(axis.title.y=element_blank(),
        axis.title.x=element_text(size = 17),
        axis.ticks.y=element_blank(),
        strip.text.y = element_text(angle = 180, hjust = 1),
        line = element_blank(),
        axis.text.x = element_text(size = 17),
        axis.text.y = element_text(size = 17))+
  scale_x_continuous( expand = c(0.01, 0)) +
  scale_y_discrete(expand = c(0.001, 0))+
  xlab("Temp (C)")
rmo.ridge
#mul
mul.ridge <- ggplot()+
  geom_density_ridges2(mul.r,fill = c('turquoise'),
                      mapping = aes(x = Value,
                                    y=site,
                                    scale=1))+
  theme_classic()+
  theme(axis.title.y=element_blank(),
        axis.title.x=element_text(size = 17),
        axis.ticks.y=element_blank(),
        strip.text.y = element_text(angle = 180, hjust = 1),
        line = element_blank(),
        axis.text.x = element_text(size = 17),
        axis.text.y = element_text(size = 17))+
  scale_x_continuous( expand = c(0.01, 0)) +
  scale_y_discrete(expand = c(0.001, 0))+
  xlab("Temp (C)")
mul.ridge
#gg
gg.ridge <- ggplot()+
  geom_density_ridges2(gg.r,fill = c('firebrick1'),
                      mapping = aes(x = Value,
                                    y=site,
                                    scale=1))+
  theme_classic()+
  theme(axis.title.y=element_blank(),
        axis.title.x=element_text(size = 17),
        axis.ticks.y=element_blank(),
        strip.text.y = element_text(angle = 180, hjust = 1),
        line = element_blank(),
        axis.text.x = element_text(size = 17),
        axis.text.y = element_text(size = 17))+
  scale_x_continuous( expand = c(0.01, 0)) +
  scale_y_discrete(expand = c(0.001, 0), 
                   labels =c("W600" = "Head (W)",
                             "W400"="Downstream (W)",
                             "LS180"="Head (LS)",
                             "LS0"="Downstream (LS)",
                             "GC300"="Head (GC)",
                             ))+
  xlab("Temp (C)")
gg.ridge
ggsave("rmo.ridge.png", plot = last_plot())
```
  
General timeseries- Not working, gave up
```{r}
#heads
head.r <- c("ULB2HA","ULB3HA", "ULB4HA", "RMO1HA", "RMO2HA", "RMO3HA", "MUL2HA",  "MUL4HB",  "MUL7HB", "W600B", "GC300B", "LS180B")
#downstream
down.r <- c("ULB2CB", "ULB3CB", "ULB4CA", "RMO1CB",  "RMO2CB",  "RMO3CB", "MUL2CB", "MUL4CA",  "MUL7CA", "W400A", "GC100B",  "LS0B")
#subset master dataset
head.r <- filter(master, site %in% head.r)
down.r <- filter(master, site %in% down.r)
#change variable names to remove A/B
head.r$site <- gsub('.{1}$', '', head.r$site)
down.r$site <- gsub('.{1}$', '', down.r$site)
#subsetting to a certain period of time
start <- mdy_hm("6-25-19 12:10")
end <- mdy_hm("7-5-19 12:10")
head.r <- filter(head.r, rnd.dates >= start)
head.r <- filter(head.r, rnd.dates <= end)

ulb.r <- filter(ulb.r, rnd.dates >= start)
ulb.r <- filter(ulb.r, rnd.dates <= end)

rmo.r <- filter(rmo.r, rnd.dates >= start)
rmo.r <- filter(rmo.r, rnd.dates <= end)

mul.r <- filter(mul.r, rnd.dates >= start)
mul.r <- filter(mul.r, rnd.dates <= end)

gg.r <- filter(gg.r, rnd.dates >= start)
gg.r <- filter(gg.r, rnd.dates <= end)
#plots
#ulb
ulb.ts <- ggplot(data = ulb.r)+
  geom_line(aes(x = rnd.dates,
                y = Value,
                color = site), size = 1.5)+
  scale_fill_brewer(palette = "Dark2")+
  ylim(9,19)+
  theme_classic()
ulb.ts
#rmo
rmo.ts <- ggplot(data = rmo.r)+
  geom_line(aes(x = rnd.dates,
                y = Value,
                color = site), size = 1.5)+
  scale_fill_brewer(palette = "Dark2")+
  ylim(9,19)+
  theme_classic()
rmo.ts
#mul
mul.ts <- ggplot(data = mul.r)+
  geom_line(aes(x = rnd.dates,
                y = Value,
                color = site), size = 1.5)+
  scale_color_brewer(palette = "Dark2")+
  ylim(9,19)+
  theme_classic()
mul.ts
#gg
gg.ts <- ggplot(data = gg.r)+
  geom_line(aes(x = rnd.dates,
                y = Value,
                color = site), size = 1.5)+
  scale_fill_brewer(palette = "Dark2")+
  ylim(9,19)+
  theme_classic()
gg.ts




#uneeded color dither i think
scale_color_manual("",
                     breaks = c(head.r),
                     values = c("turquoise","turquoise","turquoise",
                                "sienna1","sienna1","sienna1", "firebrick1",
                                "firebrick1","firebrick1",
                                "midnightblue","midnightblue","midnightblue"))+
  scale_color_manual(
  values = c("turquoise","turquoise","turquoise","sienna1","sienna1","sienna1", "firebrick1","firebrick1","firebrick1","midnightblue","midnightblue","midnightblue"),
  limits = c(head.r), breaks =c(head.r),
  name = "Relative Elevation", labels = c("High", "Medium", "Medium/Low", "Low"))+
  theme_classic()

```
  
-Head vs airT
  -mean airT vs mean waterT
  -mean airT vs mean diff or diff vs airT
```{r}
#means
master.mean <- master %>% group_by(site) %>% summarise_all(funs(mean), na.rm = TRUE)
#write.csv(master.mean, file = "temps.means.csv")
#made dataframe with means and air mean
master.mean <- read.csv("temps.means.csv")
master.mean$site <- gsub('.{1}$', '', master.mean$site)

#dont think this is necessary?
mean.r <- c("ULB2HA","ULB3HA", "ULB4HA", "RMO1HA", "RMO2HA", "RMO3HA", "MUL2HA",  "MUL4HB",  "MUL7HB", "W600B", "GC300B", "LS180B","ULB2CB", "ULB3CB", "ULB4CA", "RMO1CB",  "RMO2CB",  "RMO3CB", "MUL2CB", "MUL4CA",  "MUL7CA", "W400A", "GC100B",  "LS0B", "MULAir", "GGAir", "RMOAir", "ULBAir")

head.mean.plot <- ggplot(data = master.mean)+
  geom_point(aes(x = airmean,
                y = wtmean,
                color = loc,
                shape = type))+
  theme(axis.title.x=element_text(size = 17),
        axis.title.y=element_text(size = 17),
       axis.text.x = element_text(size = 17),
        axis.text.y = element_text(size = 17))+
  theme_classic()
head.mean.plot
ggsave("mean.plot.png", plot = last_plot())
#head vs airT
ulb.head <- c("ULB2HA","ULB3HA", "ULB4HA", "ULBAir") 
rmo.head <- c("RMO1HA", "RMO2HA", "RMO3HA", "RMOAir") 
mul.head <- c("MUL2HA",  "MUL4HB",  "MUL7HB", "MULAir") 
gg.head <- c("W600B", "GC300B", "LS180B", "GGAir")

ulb.head <- filter(master, site %in% ulb.head) 
rmo.head <- filter(master, site %in% rmo.head)
mul.head <- filter(master, site %in% mul.head) 
gg.head <- filter(master, site %in% gg.head)

ulb.head <- ulb.head %>% select(Value, site)
rmo.head <- rmo.head %>% select(Value, site)
mul.head <- mul.head %>% select(Value, site)
gg.head <- gg.head %>% select(Value, site)




ulb.tall.diffs <- ulb.diffs %>% gather(site, temp, -ULBAir)

```
  
Basic time series
```{r}
#formatting time to beginning and end of deployment period
start <- mdy_hm("6-25-19 12:10")
end <- mdy_hm("7-5-19 12:10")
timeseries <- filter(master, rnd.dates >= start)
timeseries <- filter(master, rnd.dates <= end)

all.ts <- c("ULB2HA","ULB3HA", "ULB4HA", "RMO1HA", "RMO2HA", "RMO3HA", "MUL2HA",  "MUL4HB",  "MUL7HB", "W600B", "GC300B", "LS180B","ULB2CB", "ULB3CB", "ULB4CA", "RMO1CB",  "RMO2CB",  "RMO3CB", "MUL2CB", "MUL4CA",  "MUL7CA", "W400A", "GC100B",  "LS0B", "MULAir", "GGAir", "RMOAir", "ULBAir")

timeseries <- timeseries %>% filter(site %in% all.ts)
timeseries$site <- gsub('.{1}$', '', timeseries$site)
timeseries$site <- gsub('.{1}$', '', timeseries$site)

ulb.ts <- timeseries %>% filter(shed == "ULB" & type != "air")
mul.ts <- timeseries %>% filter(shed == "MUL" & type != "air")
rmo.ts <- timeseries %>% filter(shed == "RMO" & type != "air")
gg.ts <- timeseries %>% filter(shed == "GG" & type != "air")
#ulb
rmo.ts.plot <- ggplot(data = rmo.ts)+
  geom_line(aes(x = rnd.dates,
                y = Value,
                
                color = site,
                linetype = type), 
            size = 1.5)+
  scale_linetype_manual(labels = c("Head", "Downstream"),
                        values=c("solid", "dotted"),
                        name = "Location")+
   scale_color_brewer(palette = "Dark2",
                     name = "Stream")+
  xlab( " ")+
  ylab("Temperature (C)")+
  ylim(9, 19)+
  theme_classic()+
  theme(text= element_text(size=17),
        axis.text.x = element_text(size = 17),
        axis.text.y = element_text(size = 17))
rmo.ts.plot
#rmo
ulb.ts.plot <- ggplot(data = ulb.ts)+
  geom_line(aes(x = rnd.dates,
                y = Value,
                color = site,
                linetype = type), 
            size = 1.5)+
  scale_color_brewer(palette = "Dark2",
                     name = "Stream")+
  scale_linetype_manual(values=c("solid", "dotted"),
                        name = "Location",
                        labels = c("Head", "Downstream"))+
  xlab( " ")+
  ylab("Temperature (C)")+
  ylim(9, 19)+
  theme_classic()+
  theme(text= element_text(size=17),
        axis.text.x = element_text(size = 17),
        axis.text.y = element_text(size = 17))+
  guides(color = guide_legend(order = 1), 
              linetype = guide_legend(order = 2))
ulb.ts.plot 
#mul
mul.ts.plot <- ggplot(data = mul.ts)+
  geom_line(aes(x = rnd.dates,
                y = Value,
                color = site,
                linetype = type), 
            size = 1.5)+
  scale_color_brewer(palette = "Dark2",
                     name = "Stream")+
  scale_linetype_manual(values=c("solid", "dotted"),
                        name = "Location",
                        labels = c("Head", "Downstream"))+
  xlab( " ")+
  ylab("Temperature (C)")+
  ylim(9, 19)+
  theme_classic()+
  theme(text= element_text(size=17),
        axis.text.x = element_text(size = 17),
        axis.text.y = element_text(size = 17))
mul.ts.plot
#gg
gg.names <- data.frame("names" =c("Wind","Glacier", "Glacier","Landslide","Wind","Landslide"), 
                       "site" = c("W40","GC10","GC30","LS18","W60","LS"))
gg.ts <- gg.ts %>% inner_join(gg.names, by = "site")

gg.ts.plot <- ggplot(data = gg.ts, aes(x = rnd.dates,
                y = Value,
                color = names,
                linetype = type))+
  geom_line(size = 1.5)+
  scale_color_brewer(palette = "Dark2",
                     name = "Stream")+
  scale_linetype_manual(values=c("solid", "dotted"),
                        name = "Location",
                        labels = c("Head", "Downstream"))+
  xlab( " ")+
  ylab("Temperature (C)")+
  ylim(9, 19)+
  theme_classic()+
  theme(text= element_text(size=17),
        axis.text.x = element_text(size = 17),
        axis.text.y = element_text(size = 17))
gg.ts.plot




ggsave("ulb.ts.png", plot = ulb.ts.plot, width = 8, height = 5, units = c("in"))
ggsave("mul.ts.png", plot = mul.ts.plot, width = 8, height = 5, units = c("in"))
ggsave("rmo.ts.png", plot = rmo.ts.plot, width = 8, height = 5, units = c("in"))
ggsave("gg.ts.png", plot = gg.ts.plot, width = 8, height = 5, units = c("in"))

```

